---
title: 'Calibration Report: Low N Sedimentary Site Base Case'
author: "Kaveh Gholamhossein Siah"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  pdf_document:
    toc_depth: 3
    extra_dependencies: "subfig"
    
    
geometry: margin=2 cm
fig_caption: yes
---
<br><br><br>

\newpage
\tableofcontents
\listoffigures
\listoftables
\newpage


```{r global_options, include=FALSE, message=FALSE}
#This global option holds figures in the correct place (stops floating in pdf)
knitr::opts_chunk$set(fig.pos = 'H')

```


```{r, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
library(kableExtra)
library(ggplot2)
library(dplyr)
library(captioner)
library(car)
library(janitor)
library(scales)
library(reshape2)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}

source("~/Project_Master/Test_Rep/Code/LN_SED/Base/Weathering_LN_SED_Mutator.R")

source("~/Project_Master/Test_Rep/Code/LN_SED/Base/Soil_Soln_LN_SED_Mutator.R")

source("~/Project_Master/Test_Rep/Code/LN_SED/Base/Litter_Pool_Mutator.R")

source("~/Project_Master/Test_Rep/Code/LN_SED/Base/TreeNut_LN_SED_Mutator.R")

source("~/Project_Master/Test_Rep/Code/LN_SED/Base/CEC_Mutator.R")

source("~/Project_Master/Test_Rep/Code/LN_SED/Base/AEC_Mutator.R")

source("~/Project_Master/Test_Rep/Code/LN_SED/Base/Analysis_1_Mutator.R")

source("~/Project_Master/Test_Rep/Code/LN_SED/Base/Hydro_Mutator.R")

source("~/Project_Master/Test_Rep/Code/LN_SED/Base/SOM_Mutator.R")





                                    ##Load Data, edit data as needed##
#umol/L
Cal_Pretable_Parent<-read.csv2("~/Project_Master/Test_Rep/Output/Calibration/Output_LN_SED/Edited Data/Soil_Solution_All2.csv", header=TRUE)
Cal_Pretable_SS<-Cal_Pretable_Parent %>% filter(group_id %in% c("10", "11", "12", "13", "14", "15", "16", "17"))
Cal_Pretable_SS$group_id<-as.character(Cal_Pretable_SS$group_id)


#Kg/ha
Cal_Pretable_LL<-Cal_Pretable_Parent %>% filter(group_id %in% c("1", "2", "3", "4", "5", "6", "7", "8"))
Cal_Pretable_LL$group_id<-as.character(Cal_Pretable_LL$group_id)


Cal_Pretable_SS_Yr<-Cal_Pretable_SS %>% group_by(group_id, YEAR) %>% summarise(across(Ca:HR, ~mean(.x, na.rm=TRUE)))

Cal_Pretable_W<-read.csv2("~/Project_Master/Test_Rep/Output/Calibration/Output_LN_SED/Edited Data/Weathering_All.csv", header=TRUE)

Litter_Pretable<-read.csv2("~/Project_Master/Test_Rep/Output/Calibration/Output_LN_SED/Edited Data/Litter_Pool.csv", header=TRUE)
Litter_Pretable$Date<-as.Date(as.character(Litter_Pretable$Date))

Tree_Nut_All<-read.csv2("~/Project_Master/Test_Rep/Output/Calibration/Output_LN_SED/Edited Data/Tree_Nut_All.csv", header=TRUE)


Litter_Fall<-read.csv2("~/Project_Master/Test_Rep/Output/Calibration/Output_LN_SED/Edited Data/Litter_Fall.csv", header=TRUE)
Litter_Fall$Date<-as.Date(Litter_Fall$Date)

Analysis_1<-read.csv2("~/Project_Master/Test_Rep/Output/Calibration/Output_LN_SED/Edited Data/Analysis_1.csv", header=TRUE)

CEC_All<-read.csv2("~/Project_Master/Test_Rep/Output/Calibration/Output_LN_SED/Edited Data/CEC_All.csv", header=TRUE)
CEC_All$group_id<-as.factor(CEC_All$group_id)

AEC_All<-read.csv2("~/Project_Master/Test_Rep/Output/Calibration/Output_LN_SED/Edited Data/AEC_All.csv", header=TRUE)

Lys_Table<-read.csv2("~/Project_Master/Test_Rep/Data/Base Sites/NutsForSEDLN/LN_SED_Lys_Table.csv")

Hydro_Table<-read.csv2("~/Project_Master/Test_Rep/Output/Calibration/Output_LN_SED/Edited Data/Hydrology.csv", header=TRUE)
Hydro_Table$Date<-as.Date(Hydro_Table$Date)

SOM<-read.csv2("~/Project_Master/Test_Rep/Output/Calibration/Output_LN_SED/Edited Data/SOM.csv")
SOM$Date<-as.Date(SOM$Date)

Lys_Leaching<-read.csv2("~/Project_Master/Test_Rep/Data/Base Sites/NutsForSEDLN/LN_SED_Leaching_Lys.csv")

                                            ##Load Functions for Analysis##

source("~/Project_Master/Test_Rep/Code/Functions/Tabulator.R")
source("~/Project_Master/Test_Rep/Code/Functions/Grapher_Cal_Soil_R.R")
source("~/Project_Master/Test_Rep/Code/Functions/Grapher_Cal_Weathering.R")
source("~/Project_Master/Test_Rep/Code/Functions/Grapher_Cal_SOM.R")
source("~/Project_Master/Test_Rep/Code/Functions/Grapher_Litter.R")
source("~/Project_Master/Test_Rep/Code/Functions/Grapher_Bio_Compart.R")
source("~/Project_Master/Test_Rep/Code/Functions/LL_1M_Func.R")
source("~/Project_Master/Test_Rep/Code/Functions/Grapher_Analysis_I.R")
source("~/Project_Master/Test_Rep/Code/Functions/Grapher_CEC_AEC.R")


```

### Hydrology

```{r, echo=FALSE, message=FALSE, fig.show="hold", out.width="50%", message=FALSE, fig.ncol=2}

Hydro_Table2<-Hydro_Table%>% filter(Year %in% 2005)

Hydro_Plot<-ggplot(Hydro_Table2, aes(x=Date, y=AET))+geom_line()

Hydro_Plot

RF_Mut<-Hydro_Table %>% group_by (Year) %>% summarise(across(RF:In, ~sum(.x, na.rm = TRUE)))
RF_Plot<-ggplot(RF_Mut, aes(x=Year, y=RF))+geom_line()
RF_Plot
```




### Soil Solution Results
<br>

```{r, message=FALSE, echo=FALSE, results="hide", include=FALSE}

                                               ##Table 1##
SS_Reliable_Avg<-Tab_Func_SS_Reliable(Cal_Pretable_SS)

SS_Reliable_Avg<-mutate(SS_Reliable_Avg, group_id=recode(group_id, "'10'='Layer 1' ; '11'='Layer 2' ; '12'='Layer 3' ; '13'='Layer 4'; '14'='Layer 5'; '15'='Layer 6'; '16'='Layer 7'; '17'='Layer 8'")) %>% select(-X)

SS_Reliable_Avg %>% mutate_if(is.character, format, digits=3,nsmall = 0) %>%
  kbl(caption = "Average Monthly Soil Solution Concentration (2005-2006)", col.names=c("Soil Layer","Month", "Ca", "Mg", "K", "Na", "NO3", "NH4", "SO4", "Cl", "PO4", "DOC", "Al", "Si", "H+", "pH", "R", "HR"), "latex", escape = FALSE) %>%
  t(.)%>% kable_styling(latex_options = c("striped", "scale_down", "hold_position")) %>% 
    kable_classic(full_width = F, html_font = "Times") %>% add_header_above(c(" "=2,  "$\\\\u$mol/L"=16))
```

```{r, echo=FALSE, message=FALSE}
##Average 2005-2006 per layer

Reliable_Table<-SS_Reliable_Avg %>% ungroup(Month) %>% group_by(group_id) %>% summarise(across(Ca:HR, ~ mean(.x, na.rm = TRUE)))

#Change pH average (else it won't make sense!)
Reliable_Table$pH = -log(Reliable_Table$H*10^-6, 10)

Reliable_Table %>% mutate_if(is.numeric, format, digits=3,nsmall = 0) %>%
  kbl(caption = "Average Soil Solution Concentrations of Reliable Months (2005-2006)", col.names=c("Soil Layer", "Ca", "Mg", "K", "Na", "NO3", "NH4", "SO4", "Cl", "PO4", "DOC", "Al", "Si", "H+", "pH", "R", "HR"), align = "l", format="latex", booktabs = TRUE, escape = FALSE) %>%t(.)%>% kable_styling(latex_options = c("striped", "scale_down", "hold_position")) %>%
    kable_classic(full_width = F, html_font = "Times") %>% add_header_above(c(" "=1,  "$\\\\mu$mol/L"=16), escape=FALSE)
```

<br>

```{r echo=FALSE, message=FALSE}

Lys_Table[c(1:26)]<-lapply(Lys_Table[c(1:26)], as.numeric)

Better_Names<-c("Layer",	"Ca",	"Ca SD"	, "Mg",	"Mg SD"	, "K",	"K SD",	 "Na"	,"Na SD"	, "NO3",	"NO3 SD",	 "NH4",	"NH4 SD",	 "SO4",	"SO4 SD",	 "Cl",	"Cl SD",	 "$P^a$",	"P SD"	, "DOC"	,"DOC SD"	, "$Al^b$",	"Al SD"	, "$Si^c$"	,"Si SD", "$pH^d$")

Lys_Table %>% mutate_if(is.numeric, format, digits=2, nsmall= 0) %>%
  kbl(caption = "Lysimeter Measured Soil Solution Concentrations of Reliable Months (2005)", col.names=Better_Names,         format="latex", booktabs=TRUE, escape=FALSE, align="c") %>% t(.) %>% kable_styling(latex_options = c("striped", "scale_down",     "hold_position")) %>% 
         kable_styling(font_size = 12) %>% 
              kable_classic(full_width = F, html_font = "Times") %>% landscape() %>%
                        footnote(alphabet=c("Average based on TP annual average", "Does not distinguish between organic-Al and free Al", "Model does   not simulate Si uptake", "From Hynicka et al., 2017 (10-50cm) extrapolated to 1m"))


```

<br>

```{r, echo=FALSE, message=FALSE}

Sim_Lysimeter_Flux<-Cal_Pretable_LL %>% filter(group_id %in% c("2", "8")) %>% group_by(group_id, YEAR) %>% summarise(across(Ca:HR, ~sum(.x, na.rm=TRUE))) %>% select(-H, -pH, -R, -HR) %>% filter (YEAR %in% c("2005", "2006")) %>% rename(Depth="group_id")


Sim_Lysimeter_Flux %>% mutate_if(is.numeric, format, digits=2, nsmall= 0) %>%
  kbl(caption = "Simulated Lysimeter Fluxes by Depth (2005-2006)", format="latex", booktabs=TRUE, escape=FALSE, align="c") %>% t(.) %>% kable_styling(latex_options = c("striped", "scale_down", "HOLD_position")) %>% 
         kable_styling(font_size = 12) %>% kable_classic(full_width = F, html_font = "Times")


```

<br>

```{r, echo=FALSE, message=FALSE}

Lys_Leaching %>% mutate_if(is.numeric, format, digits=2, nsmall= 0) %>%
  kbl(caption="Actual Average Lysimeter Fluxes (2005)", format="latex", booktabs=TRUE, escape=FALSE, align="c") %>% t(.) %>%
kable_styling(latex_options = c("striped", "scale_down", "HOLD_position")) %>% landscape() %>%
         kable_styling(font_size = 12) %>% kable_classic(full_width = F, html_font = "Times")

```



<br><br><br>


```{r, echo=FALSE, fig.cap="Average Annual Calcium Concentrations by Soil Layer", figures-side, fig.show="hold", out.width="50%", message=FALSE, fig.ncol=2}

Ca_L1<-Ca_SS_L1(Cal_Pretable_SS_Yr)
Ca_L1

Ca_L2<-Ca_SS_L2(Cal_Pretable_SS_Yr)
Ca_L2


```
```{r, echo=FALSE, fig.cap="Average Annual Magnesium Concentrations by Soil Layer", fig.show="hold", out.width="50%"}
Mg_L1<-Mg_SS_L1(Cal_Pretable_SS_Yr)
Mg_L1

Mg_L2<-Mg_SS_L2(Cal_Pretable_SS_Yr)
Mg_L2
```
```{r, echo=FALSE, fig.cap="Average Annual Potassium Concentrations by Soil Layer", fig.show="hold", out.width="50%"}


K_L1<-K_SS_L1(Cal_Pretable_SS_Yr)
K_L1

K_L2<-K_SS_L2(Cal_Pretable_SS_Yr)
K_L2

```
```{r, echo=FALSE, fig.cap="Average Annual Sodium Concentrations by Soil Layer", fig.show="hold", out.width="50%"}


Na_L1<-Na_SS_L1(Cal_Pretable_SS_Yr)
Na_L1

Na_L2<-Na_SS_L2(Cal_Pretable_SS_Yr)
Na_L2


```
```{r, echo=FALSE, fig.cap="Average Annual Sulfate Concentrations by Soil Layer", fig.show="hold", out.width="50%"}
SO4_L1<-SO4_SS_L1(Cal_Pretable_SS_Yr)
SO4_L1

SO4_L2<-SO4_SS_L2(Cal_Pretable_SS_Yr)
SO4_L2

```
```{r, echo=FALSE, fig.cap="Average Annual Chloride Concentrations by Soil Layer", fig.show="hold", out.width="50%"}
Cl_L1<-Cl_SS_L1(Cal_Pretable_SS_Yr)
Cl_L1

Cl_L2<-Cl_SS_L2(Cal_Pretable_SS_Yr)
Cl_L2

```



<br><br><br>

```{r, echo=FALSE, fig.cap="Monthly Aluminum Concentrations by Soil Layer", fig.show="hold", out.width="50%"}


Al_L1<-Al_SS_L1(Cal_Pretable_SS_Yr)
Al_L1

Al_L2<-Al_SS_L2(Cal_Pretable_SS_Yr)
Al_L2

```

<br><br><br>

```{r, echo=FALSE, fig.cap="Monthly SiO2 Concentrations by Soil Layer", fig.show="hold", out.width="50%"}

Si_L1<-Si_SS_L1(Cal_Pretable_SS_Yr)
Si_L1

Si_L2<-Si_SS_L2(Cal_Pretable_SS_Yr)
Si_L2

```

<br><br><br>

```{r, echo=FALSE, fig.cap="Monthly Organic Acid Base (R-) Concentrations by Soil Layer", fig.show="hold", out.width="50%"}


R_L1<-R_SS_L1(Cal_Pretable_SS_Yr)
R_L1

R_L2<-R_SS_L2(Cal_Pretable_SS_Yr)
R_L2

```

<br><br><br>

```{r, echo=FALSE, fig.cap="Monthly pH by Soil Layer", fig.show="hold", out.width="50%"}


pH_L1<-pH_SS_L1(Cal_Pretable_SS_Yr)
pH_L1

pH_L2<-pH_SS_L2(Cal_Pretable_SS_Yr)
pH_L2

```

<br><br><br>

```{r, echo=FALSE, fig.cap="Yearly Ammonium concentration by Soil Layer", fig.show="hold", out.width="50%"}


NH4_L1<-NH4_SS_L1(Cal_Pretable_SS_Yr)
NH4_L1

NH4_L2<-NH4_SS_L2(Cal_Pretable_SS_Yr)
NH4_L2

```

<br><br><br>

```{r, echo=FALSE, fig.cap="Yearly Nitrate concentration by Soil Layer", fig.show="hold", out.width="50%"}


NO3_L1<-NO3_SS_L1(Cal_Pretable_SS_Yr)
NO3_L1

NO3_L2<-NO3_SS_L2(Cal_Pretable_SS_Yr)
NO3_L2

```



<br>


### Weathering Results

```{r, echo=FALSE, message=FALSE, fig.show="hold", out.width="50%", fig.cap="Calcium Weathering (All Layer)"}
Weathering_Ca1<-Ca_W_L1(Cal_Pretable_W)
Weathering_Ca1

```

<br>
```{r, echo=FALSE, fig.show="hold", out.width="50%", fig.cap="Magnesium Weathering (All Layer)"}
Weathering_Mg1<-Mg_W_L1(Cal_Pretable_W)
Weathering_Mg1
```
<br>

```{r, echo=FALSE, fig.show="hold", out.width="50%", fig.cap="Potassium Weathering (All Layer)"}

#K Weathering
Weathering_K1<-K_W_L1(Cal_Pretable_W)
Weathering_K1
```

<br>

```{r, echo=FALSE, fig.show="hold", out.width="50%", fig.cap="Aluminum Weathering (All Layer)"}
Weathering_Al1<-Al_W_L1(Cal_Pretable_W)
Weathering_Al1
```

<br>

```{r, echo=FALSE, fig.show="hold", out.width="50%", fig.cap="Phosphate Weathering (All Layer)"}
Weathering_P1<-P_W_L1(Cal_Pretable_W)
Weathering_P1
```

<br>

```{r, echo=FALSE, fig.show="hold", out.width="50%", fig.cap="Silica Weathering (All Layer)"}
Weathering_Si1<-Si_W_L1(Cal_Pretable_W)
Weathering_Si1
```

<br>

```{r, echo=FALSE, fig.show="hold", out.width="50%", fig.cap="Sodium Weathering (All Layer)"}
Weathering_Na1<-Na_W_L1(Cal_Pretable_W)
Weathering_Na1

```


<br><br><br>

### Litter Pool Results

<br>

```{r, echo=FALSE, fig.cap="Forest Floor (O-Layer) Carbon Content Over Simulation Period", fig.show="hold", out.width="50%", fig.subcap=c("Total forest floor carbon content (kg/ha)", "Carbon content of coarse litter (kg/ha)"), fig.ncol=2}

##Should add specific fraction over time as well. 

Litter_C_All<-Litter_Graph(Litter_Pretable$C)
Litter_C_All+labs(y="C (kg/ha)")

Litter_CR<-Litter_Graph(Litter_Pretable$C_CL)
Litter_CR+labs(y="C (kg/ha)")
```
<br>


```{r, echo=FALSE, fig.cap="Forest Floor (O-Layer) Carbon Content Over Simulation Period", fig.show="hold", out.width="50%", fig.subcap=c("Carbon content of fine litter (kg/ha)", "Carbon content of humic litter (kg/ha)"), fig.ncol=2}

##Should add specific fraction over time as well. 

Litter_C_F<-Litter_Graph(Litter_Pretable$C_F)
Litter_C_F+labs(y="C (kg/ha)")

Litter_H<-Litter_Graph(Litter_Pretable$C_H)
Litter_H+labs(y="C (kg/ha)")
```

<br>

Note that the fine litter pool (the stage between humus and fresh/coarse litter) is growing in this model. This might deviate from observed behavior. 

<br>

```{r, echo=FALSE, message=FALSE, fig.show="hold", out.width="50%", fig.cap="Forest Floor/O-horizon Ca content over time (a). and net annual Ca return in litterfall (b).", fig.subcap=c("Ca Content in each litter decomposition stage (kg/ha)", "Ca net annual return in litterfall (kg/ha)")}

Ca_OH_All<-ggplot(Litter_Pretable, aes(x=Date))+geom_line(mapping=aes(y=Ca_CL, color="Coarse Litter"))+geom_line(mapping=aes(y=Ca_F, color="Fine Litter"))+geom_line(mapping=aes(y=Ca_H, color="Humic Litter"))+
  geom_line(mapping= aes(y=Ca, color="Total Litter"))+
  labs(y="Ca (kg/ha)", color="Litter Type")

Ca_OH_All

#Mutate Litter_Fall so it's on a yearly time step; can't use the flux data because it is unfortunately specified far below this code 

Litter_Fall_Year<-Litter_Fall %>% group_by(Year) %>% summarise(across(N:P, ~sum(.x, na.rm= TRUE)))

Ca_LF.G<-ggplot(Litter_Fall_Year, aes(x=Year, y=Ca, color="Ca Litterfall Return"))+geom_line()
Ca_LF.G+theme(legend.title = element_blank())

```
<br>

### Soil Organic Matter Results

```{r, echo=FALSE, message=FALSE, fig.show="hold"}
SOM<-SOM %>%group_by(Year, group_id)%>% summarize(across(C:S, ~mean(.x, na.rm = TRUE)))

SOM_C<-ggplot(SOM, aes(x=Year, y=C,color=group_id))+geom_line()
SOM_C

```

<br>


```{r, echo=FALSE, message=FALSE, fig.show="hold", out.width="50%", fig.cap="Forest Floor/O-horizon Mg content over time (a). and net annual Mg return in litterfall (b).", fig.subcap=c("Mg Content in each litter decomposition stage (kg/ha)", "Mg net annual return in litterfall (kg/ha)")}

Mg_OH_All<-ggplot(Litter_Pretable, aes(x=Date))+geom_line(mapping=aes(y=Mg_CL, color="Coarse Litter"))+geom_line(mapping=aes(y=Mg_F, color="Fine Litter"))+geom_line(mapping=aes(y=Mg_H, color="Humic Litter"))+
  geom_line(mapping= aes(y=Mg, color="Total Litter"))+
  labs(y="Mg (kg/ha)", color="Litter Type")

Mg_OH_All

#Mutate Litter_Fall so it's on a yearly time step; can't use the flux data because it is unfortunately specified far below this code 

Litter_Fall_Year<-Litter_Fall %>% group_by(Year) %>% summarise(across(N:P, ~sum(.x, na.rm= TRUE)))

Mg_LF.G<-ggplot(Litter_Fall_Year, aes(x=Year, y=Mg, color="Mg Litterfall Return"))+geom_line()
Mg_LF.G+theme(legend.title = element_blank())

```

<br>


```{r, echo=FALSE, message=FALSE, fig.show="hold", out.width="50%", fig.cap="Forest Floor/O-horizon K content over time (a). and net annual K return in litterfall (b).", fig.subcap=c("K Content in each litter decomposition stage (kg/ha)", "K net annual return in litterfall (kg/ha)")}

K_OH_All<-ggplot(Litter_Pretable, aes(x=Date))+geom_line(mapping=aes(y=K_CL, color="Coarse Litter"))+geom_line(mapping=aes(y=K_F, color="Fine Litter"))+geom_line(mapping=aes(y=K_H, color="Humic Litter"))+
  geom_line(mapping= aes(y=K, color="Total Litter"))+
  labs(y="K (kg/ha)", color="Litter Type")

K_OH_All

#Mutate Litter_Fall so it's on a yearly time step; can't use the flux data because it is unfortunately specified far below this code 

Litter_Fall_Year<-Litter_Fall %>% group_by(Year) %>% summarise(across(N:P, ~sum(.x, na.rm= TRUE)))

K_LF.G<-ggplot(Litter_Fall_Year, aes(x=Year, y=K, color="K Litterfall Return"))+geom_line()
K_LF.G+theme(legend.title = element_blank())

```

<br>

```{r, echo=FALSE, message=FALSE, fig.show="hold", out.width="50%", fig.cap="Forest Floor/O-horizon S content over time (a). and net annual S return in litterfall (b).", fig.subcap=c("S Content in each litter decomposition stage (kg/ha)", "S net annual return in litterfall (kg/ha)")}

S_OH_All<-ggplot(Litter_Pretable, aes(x=Date))+geom_line(mapping=aes(y=S_CL, color="Coarse Litter"))+geom_line(mapping=aes(y=S_F, color="Fine Litter"))+geom_line(mapping=aes(y=S_H, color="Humic Litter"))+
  geom_line(mapping= aes(y=S, color="Total Litter"))+
  labs(y="S (kg/ha)", color="Litter Type")

S_OH_All

#Mutate Litter_Fall so it's on a yearly time step; can't use the flux data because it is unfortunately specified far below this code 

Litter_Fall_Year<-Litter_Fall %>% group_by(Year) %>% summarise(across(N:P, ~sum(.x, na.rm= TRUE)))

S_LF.G<-ggplot(Litter_Fall_Year, aes(x=Year, y=S, color="S Litterfall Return"))+geom_line()
S_LF.G+theme(legend.title = element_blank())

```

<br>

```{r, echo=FALSE, message=FALSE, fig.show="hold", out.width="50%", fig.cap="Forest Floor/O-horizon P content over time (a). and net annual P return in litterfall (b).", fig.subcap=c("P Content in each litter decomposition stage (kg/ha)", "P net annual return in litterfall (kg/ha)")}

P_OH_All<-ggplot(Litter_Pretable, aes(x=Date))+geom_line(mapping=aes(y=P_CL, color="Coarse Litter"))+geom_line(mapping=aes(y=P_F, color="Fine Litter"))+geom_line(mapping=aes(y=P_H, color="Humic Litter"))+
  geom_line(mapping= aes(y=P, color="Total Litter"))+
  labs(y="P (kg/ha)", color="Litter Type")

P_OH_All

#Mutate Litter_Fall so it's on a yearly time step; can't use the flux data because it is unfortunately specified far below this code 

Litter_Fall_Year<-Litter_Fall %>% group_by(Year) %>% summarise(across(N:P, ~sum(.x, na.rm= TRUE)))

P_LF.G<-ggplot(Litter_Fall_Year, aes(x=Year, y=P, color="P Litterfall Return"))+geom_line()
P_LF.G+theme(legend.title = element_blank())

```

<br>

```{r, echo=FALSE, message=FALSE, fig.show="hold", out.width="50%", fig.cap="Forest Floor/O-horizon N content over time (a). and net annual N return in litterfall (b).", fig.subcap=c("N Content in each litter decomposition stage (kg/ha)", "N net annual return in litterfall (kg/ha)")}

N_OH_All<-ggplot(Litter_Pretable, aes(x=Date))+geom_line(mapping=aes(y=N_CL, color="Coarse Litter"))+geom_line(mapping=aes(y=N_F, color="Fine Litter"))+geom_line(mapping=aes(y=N_H, color="Humic Litter"))+
  geom_line(mapping= aes(y=N, color="Total Litter"))+
  labs(y="N (kg/ha)", color="Litter Type")

N_OH_All

#Mutate Litter_Fall so it's on a yearly time step; can't use the flux data because it is unfortunately specified far below this code 

Litter_Fall_Year<-Litter_Fall %>% group_by(Year) %>% summarise(across(N:N, ~sum(.x, na.rm= TRUE)))

N_LF.G<-ggplot(Litter_Fall_Year, aes(x=Year, y=N, color="N Litterfall Return"))+geom_line()
N_LF.G+theme(legend.title = element_blank())

```

<br>

I plotted the litterfall return rate and the O-horizons next to each other to show that the inability of the O-horizon to build up certain nutrients is not an issue with nutrient release (these values can be set to be very low, such as 0.05 for Ca and Mg, and losses are still observed), but likely due to a gradual depletion of the soil for specific nutrients. The site builds up with N in the O-horizon, and this likely implies that the system is not limited by N, but that base cations are becoming increasingly limited over time, with the exception of K. 

### Tree Nutrient Content
<br>

```{r, echo=FALSE, message=FALSE, fig.cap="Base Cation Nutrient Content in Simulated Forest", fig.align='center', out.width="50%", fig.show="hold", fig.ncol=2, fig.subcap=c('Calcium content in each biomass compartment', 'Magnesium content in each biomass compartment', 'Potassium content in each biomass compartment')}

#By doing selection here, we allow for 1 file to be read from rather than multiple. 

#Ca

Tree_Nut_Ca<-Tree_Nut_All %>% select(Ca_F, Ca_Bol, Ca_Brh, Ca_Brk, YEAR, Month)

Tree_Nut_Ca<-Tree_Nut_Ca %>% mutate(Date= make_date(YEAR, Month)) %>% select (-YEAR, -Month) %>% group_by(Date)

Tree_Nut_Ca_Melt<-Tree_Nut_Ca_Melt<-melt(Tree_Nut_Ca, id.vars= c("Date"))

Ca_Nut<-ggplot(Tree_Nut_Ca_Melt, aes(x=Date, y=value, fill=variable))+geom_area()+labs(y="Ca Content in Biomass: kg/ha")+ scale_fill_discrete(name="Biomass Compartment", labels=c("Foliage", "Bole", "Branch", "Bark"))
Ca_Nut

#Mg
Tree_Nut_Mg<-Tree_Nut_All %>% select(Mg_F, Mg_Bol, Mg_Brh, Mg_Brk, YEAR, Month)

Tree_Nut_Mg<-Tree_Nut_Mg %>% mutate(Date= make_date(YEAR, Month)) %>% select (-YEAR, -Month) %>% group_by(Date)

Tree_Nut_Mg_Melt<-Tree_Nut_Mg_Melt<-melt(Tree_Nut_Mg, id.vars= c("Date"))

Mg_Nut<-ggplot(Tree_Nut_Mg_Melt, aes(x=Date, y=value, fill=variable))+geom_area()+labs(y="Mg Content in Biomass: kg/ha")+ scale_fill_discrete(name="Biomass Compartment", labels=c("Foliage", "Bole", "Branch", "Bark"))
Mg_Nut


#K

Tree_Nut_K<-Tree_Nut_All %>% select(K_F, K_Bol, K_Brh, K_Brk, YEAR, Month)

Tree_Nut_K<-Tree_Nut_K %>% mutate(Date= make_date(YEAR, Month)) %>% select (-YEAR, -Month) %>% group_by(Date)

Tree_Nut_K_Melt<-Tree_Nut_K_Melt<-melt(Tree_Nut_K, id.vars= c("Date"))

K_Nut<-ggplot(Tree_Nut_K_Melt, aes(x=Date, y=value, fill=variable))+geom_area()+labs(y="K Content in Biomass: kg/ha")+ scale_fill_discrete(name="Biomass Compartment", labels=c("Foliage", "Bole", "Branch", "Bark"))
K_Nut

```
<br>
```{r, echo=FALSE, message=FALSE, fig.cap="N, S, and P Nutrient Contents and biomass per compartment", fig.align='center', out.width="50%", fig.show="hold", fig.ncol=2, fig.subcap=c('Nitrogen content in each biomass compartment', 'Sulfur content in each biomass compartment', 'Phosphorous content in each biomass compartment', 'Biomass of each compartment')}

#N

Tree_Nut_N<-Tree_Nut_All %>% select(N_F, N_Bol, N_Brk, YEAR, Month, N_Brh)

Tree_Nut_N<-Tree_Nut_N %>% mutate(Date= make_date(YEAR, Month)) %>% select (-YEAR, -Month) %>% group_by(Date)

Tree_Nut_N_Melt<-Tree_Nut_N_Melt<-melt(Tree_Nut_N, id.vars= c("Date"))

N_Nut<-ggplot(Tree_Nut_N_Melt, aes(x=Date, y=value, fill=variable))+geom_area()+labs(y="N Content in Biomass: kg/ha")+ scale_fill_discrete(name="Biomass Compartment", labels=c("Foliage", "Bole", "Branch", "Bark"))
N_Nut

#S
Tree_Nut_S<-Tree_Nut_All %>% select(S_F, S_Bol, S_Brh, S_Brk, YEAR, Month)

Tree_Nut_S<-Tree_Nut_S %>% mutate(Date= make_date(YEAR, Month)) %>% select (-YEAR, -Month) %>% group_by(Date)

Tree_Nut_S_Melt<-Tree_Nut_S_Melt<-melt(Tree_Nut_S, id.vars= c("Date"))

S_Nut<-ggplot(Tree_Nut_S_Melt, aes(x=Date, y=value, fill=variable))+geom_area()+labs(y="S Content in Biomass: kg/ha")+ scale_fill_discrete(name="Biomass Compartment", labels=c("Foliage", "Bole", "Branch", "Bark"))
S_Nut

#P
Tree_Nut_P<-Tree_Nut_All %>% select(P_F, P_Bol, P_Brh, P_Brk, YEAR, Month)

Tree_Nut_P<-Tree_Nut_P %>% mutate(Date= make_date(YEAR, Month)) %>% select (-YEAR, -Month) %>% group_by(Date)

Tree_Nut_P_Melt<-Tree_Nut_P_Melt<-melt(Tree_Nut_P, id.vars= c("Date"))

Tree_Nut_P_Melt$value<-as.numeric(Tree_Nut_P_Melt$value)

P_Nut<-ggplot(Tree_Nut_P_Melt, aes(x=Date, y=value, fill=variable))+geom_area()+labs(y="P Content in Biomass: kg/ha")+ scale_fill_discrete(name="Biomass Compartment", labels=c("Foliage", "Bole", "Branch", "Bark"))
P_Nut

#Dry Weight/Biomass

Tree_Nut_DW<-Tree_Nut_All %>% select(DW_F, DW_Bol, DW_Brh, DW_Brk, YEAR, Month)

Tree_Nut_DW<-Tree_Nut_DW %>% mutate(Date= make_date(YEAR, Month)) %>% select (-YEAR, -Month) %>% group_by(Date)

Tree_Nut_DW_Melt<-Tree_Nut_DW_Melt<-melt(Tree_Nut_DW, id.vars= c("Date"))

DW_Nut<-ggplot(Tree_Nut_DW_Melt, aes(x=Date, y=value, fill=variable))+geom_area()+labs(y="Dry Weight of Biomass Compartments: kg/ha")+ scale_fill_discrete(name="Biomass Compartment", labels=c("Foliage", "Bole", "Branch", "Bark"))
DW_Nut
```

<br>

### Analysis 1: Stack Flux Data

```{r, echo=FALSE, message=FALSE}
#Final Mutation for Analysis 1, must be done AFTER leaching_table_1m is assigned. 

Leaching_Table_Graphable<-Tab_Func_LL_Yr(Cal_Pretable_LL)
Leaching_Table_1m<-Leaching_Table_Graphable %>% filter(group_id %in% c(8))

Analysis_Bound<- cbind(Leaching_Table_1m, Analysis_1)

Analysis_1_Ready<-Analysis_Bound %>% group_by(V1) %>% 
    mutate(Ca_Net=Ca_Wet+Ca_WTH+Ca_L_Min+Ca_SOM_Min-Ca_TU-Ca) %>%
    mutate(Mg_Net=Mg_Wet+Mg_WTH+Mg_L_Min+Mg_SOM_Min-Mg_TU-Mg) %>% 
    mutate(K_Net=K_Wet+K_WTH+K_L_Min+K_SOM_Min-K_TU-K+K_Folx) %>%
    mutate(SO4_Net=SO4_Wet+ S_L_Min+S_SOM_Min-S_TU-SO4) %>%
    mutate(N_Net=Ntot_Wet+ N_L_Min+N_SOM_Min-N_TU-SO4) %>%
    mutate(P_Net=P_WTH+ P_L_Min+P_SOM_Min-P_TU-P)

```


<br>


```{r, echo=FALSE, out.width="50%", fig.ncol=2, fig.show="hold", message=FALSE, fig.cap="Calcium input and output comparison graphs", fig.subcap=c("Ca input and output fluxes over time", "Total Average Ca input and output fluxes")}

#Make sure to define leaching table 1m before
Analysis_Bound<-Analysis_Bound %>% ungroup(YEAR) %>% select(-YEAR)

Ca_Flux<-Analysis_Bound %>% select (Ca, Ca_Wet, Ca_WTH, Ca_TU, Year, Ca_LF, Ca_L_Min)
Ca_Flux$Ca_LF<-Ca_Flux$Ca_LF*10

Ca_Melt<-melt(Ca_Flux, id.vars = c("Year") )

Ca_Stacked<-ggplot(Ca_Melt, aes(x=Year, y=value, fill=variable))+geom_area()+labs(y="Ca Flux From Ecosystem Pools: kg/ha/yr")+
   scale_fill_discrete(name = "Legend", labels = c("Leaching Flux", "Deposition", "Weathering Flux", "Total Uptake", "Litterfall Return", "Litter Mineralization"))
Ca_Stacked


Ca_Forged<-dcast(Ca_Melt, Year~variable)

Ca_Forged_Mean<-Ca_Forged %>% summarise(across(Ca:Ca_L_Min, ~mean(.x, na.rm=TRUE)))

Ca_ReForged_Mean<-melt(Ca_Forged_Mean)

Bar_Ca<-ggplot(Ca_ReForged_Mean, aes(fill=variable, y=value, x="LN SED Base Case")) + 
    geom_bar(position="stack", stat="identity")+
   scale_fill_discrete(name = "Average Ca Fluxes", labels = c("Leaching Flux", "Deposition", "Weathering Flux", "Total Uptake", "Litterfall Return", "Litter Mineralization"))+
  labs(x="Site", y=expression(Ca~kg~'*'~(ha~'*'~yr)^-1))

Bar_Ca



```

<br>

```{r, echo=FALSE, out.width="50%", fig.ncol=2, fig.show="hold", message=FALSE, fig.cap="Magnesium input and output comparison graphs", fig.subcap=c("Mg input and output fluxes over time", "Total Average Mg input and output fluxes")}

Mg_Flux<-Analysis_Bound %>% select (Mg, Mg_Wet, Mg_WTH, Mg_TU, Year, Mg_LF, Mg_L_Min)
Mg_Flux$Mg_LF<-Mg_Flux$Mg_LF*10

Mg_Melt<-melt(Mg_Flux, id.vars = c("Year") )

Mg_Stacked<-ggplot(Mg_Melt, aes(x=Year, y=value, fill=variable))+geom_area()+labs(y="Mg Flux From Ecosystem Pools: kg/ha/yr")+
   scale_fill_discrete(name = "Legend", labels = c("Leaching Flux", "Deposition", "Weathering Flux", "Total Uptake", "Litterfall Return", "Litter Mineralization"))
Mg_Stacked

Mg_Forged<-dcast(Mg_Melt, Year~variable)

Mg_Forged_Mean<-Mg_Forged %>% summarise(across(Mg:Mg_L_Min, ~mean(.x, na.rm=TRUE)))

Mg_ReForged_Mean<-melt(Mg_Forged_Mean)

Bar_Mg<-ggplot(Mg_ReForged_Mean, aes(fill=variable, y=value, x="LN SED Base Case")) + 
    geom_bar(position="stack", stat="identity")+
   scale_fill_discrete(name = "Average Mg Fluxes", labels = c("Leaching Flux", "Deposition", "Weathering Flux", "Total Uptake", "Litterfall Return", "Litter Mineralization"))+
  labs(x="Site", y=expression(Mg~kg~'*'~(ha~'*'~yr)^-1))

Bar_Mg




```

<br>

```{r, echo=FALSE, out.width="50%", fig.ncol=2, fig.show="hold", message=FALSE, fig.cap="Potassium input and output comparison graphs", fig.subcap=c("K input and output fluxes over time", "Total Average K input and output fluxes")}

K_Flux<-Analysis_Bound %>% select (K, K_Wet, K_WTH, K_TU, Year, K_LF, K_L_Min)
K_Flux$K_LF<-K_Flux$K_LF*10

K_Melt<-melt(K_Flux, id.vars = c("Year") )

K_Stacked<-ggplot(K_Melt, aes(x=Year, y=value, fill=variable))+geom_area()+labs(y="K Flux From Ecosystem Pools: kg/ha/yr")+
   scale_fill_discrete(name = "Legend", labels = c("Leaching Flux", "Deposition", "Weathering Flux", "Total Uptake", "Litterfall Return", "Litter Mineralization"))
K_Stacked

K_Forged<-dcast(K_Melt, Year~variable)

K_Forged_Mean<-K_Forged %>% summarise(across(K:K_L_Min, ~mean(.x, na.rm=TRUE)))

K_ReForged_Mean<-melt(K_Forged_Mean)

Bar_K<-ggplot(K_ReForged_Mean, aes(fill=variable, y=value, x="LN SED Base Case")) + 
    geom_bar(position="stack", stat="identity")+
   scale_fill_discrete(name = "Average K Fluxes", labels = c("Leaching Flux", "Deposition", "Weathering Flux", "Total Uptake", "Litterfall Return", "Litter Mineralization"))+
  labs(x="Site", y=expression(K~kg~'*'~(ha~'*'~yr)^-1))

Bar_K
```

<br>

```{r, fig.show="hold", echo=FALSE, out.width="50%", echo=FALSE, message=FALSE, fig.cap="Sulfur input and output comparison graphs", fig.subcap=c("S input and output fluxes over time", "Total Average S input and output fluxes")}

SO4_Flux<-Analysis_Bound %>% select (SO4, SO4_Wet, S_TU, Year, S_LF, S_L_Min)
SO4_Flux$S_LF<-SO4_Flux$S_LF*10

SO4_Melt<-melt(SO4_Flux, id.vars = c("Year") )


SO4_Stacked<-ggplot(SO4_Melt, aes(x=Year, y=value, fill=variable))+geom_area()+labs(y="SO4-S Flux From Ecosystem Pools:kg/ha/yr")+
  scale_fill_discrete(name = "Legend", labels = c("Leaching Flux", "Deposition", "Total Uptake", "Litterfall Return", "Litter Mineralization"))
SO4_Stacked

SO4_Forged<-dcast(SO4_Melt, Year~variable)

SO4_Forged_Mean<-SO4_Forged %>% summarise(across(SO4:S_L_Min, ~mean(.x, na.rm=TRUE)))

SO4_ReForged_Mean<-melt(SO4_Forged_Mean)

Bar_SO4<-ggplot(SO4_ReForged_Mean, aes(fill=variable, y=value, x="LN SED Base Case")) + 
    geom_bar(position="stack", stat="identity")+
   scale_fill_discrete(name = "Average SO4-S Fluxes", labels = c("Leaching Flux", "Deposition", "Total Uptake", "Litterfall Return", "Litter Mineralization"))+
  labs(x="Site", y=expression(SO4~kg~'*'~(ha~'*'~yr)^-1))

Bar_SO4


```

I added back a reasonably large sulfate pool, this caused enhanced S losses which were unrealistic. This likely implies that the system had too much S going through it. 
<br>

```{r, fig.show="hold", out.width="50%", echo=FALSE, message=FALSE, fig.cap="Nitrogen input and output comparison graphs", fig.subcap=c("N input and output fluxes over time", "Total Average N input and output fluxes")}


N_Flux<-Analysis_Bound %>% select (NO3, NH4, Ntot_Wet, N_TU, Year, N_LF, N_L_Min, N_SOM_Min)
N_Flux$LL<-N_Flux$NO3+N_Flux$NH4
N_Flux$N_LF<-N_Flux$N_LF*10

N_Flux<-N_Flux %>% select(-NO3, -NH4)

N_Melt<-melt(N_Flux, id.vars = c("Year"))

N_Stacked<-ggplot(N_Melt, aes(x=Year, y=value, fill=variable))+geom_area()+labs(y="N Flux From Ecosystem Pools: kg/ha/yr")+
   scale_fill_discrete(name = "Legend", labels = c("Deposition", "Total Uptake", "Litterfall Return", "Litter Mineralization", "SOM Mineralization", "Leaching Loss"))
N_Stacked

N_Forged<-dcast(N_Melt, Year~variable)

N_Forged_Mean<-N_Forged %>% summarise(across(Ntot_Wet:LL, ~mean(.x, na.rm=TRUE)))

N_ReForged_Mean<-melt(N_Forged_Mean)

Bar_N<-ggplot(N_ReForged_Mean, aes(fill=variable, y=value, x="LN SED Base Case")) + 
    geom_bar(position="stack", stat="identity")+
   scale_fill_discrete(name = "Average N Fluxes", labels = c("Deposition", "Total Uptake", "Litterfall Return", "Litter Mineralization", "SOM Mineralization", "Leaching Loss"))+
  labs(x="Site", y=expression(N~kg~'*'~(ha~'*'~yr)^-1))

Bar_N
```

Notice how SOM mineralization starts off highly negative (-358 kg/ha/yr N); implying a large net N uptake in the microbial pool. The mineralization then balances out and steadily returns N to the soil over time, behaving normally. I do need the microbial pool to help calibrate the N cycle, but I may need to reduce the CEC stabilized N and decrease the N-uptake in the microbial pool. These results likely imply too much N is going through the system and that the microbial pool is too large of an N pool. 

### Cation Exchange Capacity
```{r, echo=FALSE, out.width="50%", fig.ncol=2, fig.show="hold", message=FALSE, fig.cap="Calcium and Magnesium CEC adsorption over time", fig.subcup=c("Ca adsorption (kg/ha)", "Mg adsorption (kg/ha)")}

CEC_All$Date<-as.Date(CEC_All$Date)

CEC_Ca<-CEC_Grapher(CEC_All$Ca)
CEC_Ca+labs(y="Ca on cation exchange surfaces (kg/ha)")+ scale_x_discrete(guide = guide_axis(check.overlap = TRUE))+ scale_x_date(date_labels = "%Y")+scale_fill_discrete(name="Layer Number")

CEC_Mg<-CEC_Grapher(CEC_All$Mg)
CEC_Mg+labs(y="Mg on cation exchange surfaces (kg/ha)")+ scale_x_discrete(guide = guide_axis(check.overlap = TRUE))+ scale_x_date(date_labels = "%Y")+scale_fill_discrete(name="Layer Number")


```

<br>

```{r, echo=FALSE, out.width="50%", fig.ncol=2, fig.show="hold", message=FALSE,fig.cap="Potassium and Sodium CEC adsorption over time", fig.subcup=c("K adsorption (kg/ha)", "Na adsorption (kg/ha)")}

CEC_K<-CEC_Grapher(CEC_All$K)
CEC_K+labs(y="K on cation exchange surfaces (kg/ha)")+ scale_x_discrete(guide = guide_axis(check.overlap = TRUE))+ scale_x_date(date_labels = "%Y")+scale_fill_discrete(name="Layer Number")

CEC_Na<-CEC_Grapher(CEC_All$Na)
CEC_Na+labs(y="Na on cation exchange surfaces (kg/ha)")+ scale_x_discrete(guide = guide_axis(check.overlap = TRUE))+ scale_x_date(date_labels = "%Y")+scale_fill_discrete(name="Layer Number")

```

<br>

```{r, echo=FALSE, out.width="50%", fig.ncol=2, fig.show="hold", message=FALSE, fig.cap="Ammonium and Aluminum CEC adsorption over time", fig.subcup=c("NH4 adsorption (kg/ha)", "Al adsorption (kg/ha)")}


CEC_NH4<-CEC_Grapher(CEC_All$NH4)
CEC_NH4+labs(y="NH4 on cation exchange surfaces (kg/ha)")+ scale_x_discrete(guide = guide_axis(check.overlap = TRUE))+ scale_x_date(date_labels = "%Y")+scale_fill_discrete(name="Layer Number")

CEC_Al<-CEC_Grapher(CEC_All$Al)
CEC_Al+labs(y="Al on cation exchange surfaces (kg/ha)")+ scale_x_discrete(guide = guide_axis(check.overlap = TRUE))+ scale_x_date(date_labels = "%Y")+scale_fill_discrete(name="Layer Number")

```

<br><br><br>

### Anion Exchange Capacity 


```{r, echo=FALSE, message=FALSE, message=FALSE}


AEC_All$group_id<-as.factor(AEC_All$group_id)
AEC_All$Date<-as.Date(AEC_All$Date)

SO4_AEC<-AEC_Grapher(AEC_All$SO4)
SO4_AEC+labs(y="Soil adsorbed Sulfate (SO4-S kg/ha)")+scale_x_discrete(guide = guide_axis(check.overlap = TRUE))+scale_x_date(date_labels = "%Y")+scale_fill_discrete(name="Layer Number")


PO4_AEC<-AEC_Grapher(AEC_All$PO4)
PO4_AEC+labs(y="Soil adsorbed PO4-P (kg/ha)")+scale_x_discrete(guide = guide_axis(check.overlap = TRUE))+scale_x_date(date_labels = "%Y")+scale_fill_discrete(name="Layer Number")

Cl_AEC<-AEC_Grapher(AEC_All$Cl)

Cl_AEC+labs(y="Soil adsorbed Chloride kg/ha)")+scale_x_discrete(guide = guide_axis(check.overlap = TRUE))+scale_x_date(date_labels = "%Y")+scale_fill_discrete(name="Layer Number")

```

<br>

Phosphate seems stable, generally. It should be noted that P uptake is not being modeled in the foliage (it should remain constant so far) and that phosphate adsorption parameters are completely borrowed from the Burgundy site. As for sulfate, I purged the model of the AEC sulfate pool and relegated all soil S to the SOM organic pool. 

I further note that the ALSEA rain chemistry seems to be lacking in Na and Cl, when I completely take away Cl adsorption, I don't get anywhere near the concentration of Cl measured in the lysimeters, like I do for sulfate. 

<br>

### Other 

```{r, echo=FALSE, message=FALSE}

Litter_Fall$Dry.weight_kgha<-Litter_Fall$Dry.weight*10

Litter_Fall[c(11:16)]<-lapply(Litter_Fall[c(11:16)], as.numeric)

Litter_Fall<-Litter_Fall %>% group_by(Year) %>% select(-Date) %>%
  summarise(across(Dry.weight:Dry.weight_kgha, ~sum(.x, na.rm=TRUE)))

LF<-ggplot(Litter_Fall, aes(x=Year, y=Dry.weight_kgha))+geom_line()+labs(y="Litter Fall Dry Weight (kg/ha)")
LF

```






