---
title: 'Calibration Report: High N Basalt Site Base Case'
author: "Kaveh Gholamhossein Siah"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  pdf_document:
    toc_depth: 3
    extra_dependencies: "subfig"
    
    
geometry: margin=2 cm
fig_caption: yes
---
<br><br><br>

\newpage
\tableofcontents
\listoffigures
\listoftables
\newpage


```{r global_options, include=FALSE, message=FALSE}
#This global option holds figures in the correct place (stops floating in pdf)
knitr::opts_chunk$set(fig.pos = 'H')

```


```{r, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
library(kableExtra)
library(ggplot2)
library(dplyr)
library(captioner)
library(car)
library(janitor)
library(scales)
library(reshape2)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}

source("~/Project_Master/Test_Rep/Code/HN_BAS/Base/Weathering_Mutator.R")

source("~/Project_Master/Test_Rep/Code/HN_BAS/Base/Soil_Soln_Mutator.R")

source("~/Project_Master/Test_Rep/Code/HN_BAS/Base/Litter_Pool_Mutator.R")

source("~/Project_Master/Test_Rep/Code/HN_BAS/Base/TreeNut_Mutator.R")

source("~/Project_Master/Test_Rep/Code/HN_BAS/Base/CEC_Mutator.R")

source("~/Project_Master/Test_Rep/Code/HN_BAS/Base/AEC_Mutator.R")

source("~/Project_Master/Test_Rep/Code/HN_BAS/Base/Analysis_1_Mutator.R")

source("~/Project_Master/Test_Rep/Code/HN_BAS/Base/Hydro_Mutator.R")

source("~/Project_Master/Test_Rep/Code/HN_BAS/Base/SOM_Mutator.R")

source("~/Project_Master/Test_Rep/Code/HN_BAS/Base/Plant_Pool_Mutator.R")





                                    ##Load Data, edit data as needed##
#umol/L
Cal_Pretable_Parent<-read.csv2("~/Project_Master/Test_Rep/Output/Calibration/Output_HN_BAS/Edited Data/Soil_Solution_All2.csv", header=TRUE)
Cal_Pretable_SS<-Cal_Pretable_Parent %>% filter(group_id %in% c("10", "11", "12", "13", "14", "15", "16", "17"))
Cal_Pretable_SS$group_id<-as.character(Cal_Pretable_SS$group_id)
Cal_Pretable_SS$Date<-as.Date(Cal_Pretable_SS$Date)


#Kg/ha
Cal_Pretable_LL<-Cal_Pretable_Parent %>% filter(group_id %in% c("1", "2", "3", "4", "5", "6", "7", "8"))
Cal_Pretable_LL$group_id<-as.character(Cal_Pretable_LL$group_id)


Cal_Pretable_SS_Yr<-Cal_Pretable_SS %>% group_by(group_id, YEAR) %>% summarise(across(Ca:HR, ~mean(.x, na.rm=TRUE)))

Cal_Pretable_W<-read.csv2("~/Project_Master/Test_Rep/Output/Calibration/Output_HN_BAS/Edited Data/Weathering_All.csv", header=TRUE)
Cal_Pretable_W$Date<-as.Date(Cal_Pretable_W$Date)

Litter_Pretable<-read.csv2("~/Project_Master/Test_Rep/Output/Calibration/Output_HN_BAS/Edited Data/Litter_Pool.csv", header=TRUE)
Litter_Pretable$Date<-as.Date(as.character(Litter_Pretable$Date))

Tree_Nut_All<-read.csv2("~/Project_Master/Test_Rep/Output/Calibration/Output_HN_BAS/Edited Data/Tree_Nut_All.csv", header=TRUE)


Litter_Fall<-read.csv2("~/Project_Master/Test_Rep/Output/Calibration/Output_HN_BAS/Edited Data/Litter_Fall.csv", header=TRUE)
Litter_Fall$Date<-as.Date(Litter_Fall$Date)

Analysis_1<-read.csv2("~/Project_Master/Test_Rep/Output/Calibration/Output_HN_BAS/Edited Data/Analysis_1.csv", header=TRUE)

CEC_All<-read.csv2("~/Project_Master/Test_Rep/Output/Calibration/Output_HN_BAS/Edited Data/CEC_All.csv", header=TRUE)
CEC_All$group_id<-as.factor(CEC_All$group_id)

AEC_All<-read.csv2("~/Project_Master/Test_Rep/Output/Calibration/Output_HN_BAS/Edited Data/AEC_All.csv", header=TRUE)


Hydro_Table<-read.csv2("~/Project_Master/Test_Rep/Output/Calibration/Output_HN_BAS/Edited Data/Hydrology.csv", header=TRUE)
Hydro_Table$Date<-as.Date(Hydro_Table$Date)

SOM<-read.csv2("~/Project_Master/Test_Rep/Output/Calibration/Output_HN_BAS/Edited Data/SOM.csv")
SOM$Date<-as.Date(SOM$Date)


Plant_Pool<-read.csv2("~/Project_Master/Test_Rep/Output/Calibration/Output_HN_BAS/Edited Data/Plant_Pool.csv")

                                            ##Load Functions for Analysis##

source("~/Project_Master/Test_Rep/Code/Functions/Tabulator.R")
source("~/Project_Master/Test_Rep/Code/Functions/Grapher_Cal_Soil_R.R")
source("~/Project_Master/Test_Rep/Code/Functions/Grapher_Cal_Weathering.R")
source("~/Project_Master/Test_Rep/Code/Functions/Grapher_Cal_SOM.R")
source("~/Project_Master/Test_Rep/Code/Functions/Grapher_Litter.R")
source("~/Project_Master/Test_Rep/Code/Functions/Grapher_Bio_Compart.R")
source("~/Project_Master/Test_Rep/Code/Functions/LL_1M_Func.R")
source("~/Project_Master/Test_Rep/Code/Functions/Grapher_Analysis_I.R")
source("~/Project_Master/Test_Rep/Code/Functions/Grapher_CEC_AEC.R")
source("~/Project_master/Test_Rep/Code/Functions/Grapher_PP.R")


```

### Hydrology

```{r, echo=FALSE, message=FALSE, fig.show="hold", out.width="50%", message=FALSE, fig.ncol=2}

Hydro_Plot<-ggplot(Hydro_Table, aes(x=Date, y=AET))+geom_line()

Hydro_Plot

RF_Mut<-Hydro_Table %>% group_by (Year) %>% summarise(across(RF:In, ~sum(.x, na.rm = TRUE)))
RF_Plot<-ggplot(RF_Mut, aes(x=Year, y=RF))+geom_line()
RF_Plot
```




### Soil Solution Results
<br>

```{r, message=FALSE, echo=FALSE, results="hide", include=FALSE}

                                               ##Table 1##
SS_Reliable_Avg<-Tab_Func_SS_Reliable(Cal_Pretable_SS)

SS_Reliable_Avg<-mutate(SS_Reliable_Avg, group_id=recode(group_id, "'10'='Layer 1' ; '11'='Layer 2' ; '12'='Layer 3' ; '13'='Layer 4'; '14'='Layer 5'; '15'='Layer 6'; '16'='Layer 7'; '17'='Layer 8'")) %>% select(-X)

SS_Reliable_Avg %>% mutate_if(is.character, format, digits=3,nsmall = 0) %>%
  kbl(caption = "Average Monthly Soil Solution Concentration (2005-2006)", col.names=c("Soil Layer","Month", "Ca", "Mg", "K", "Na", "NO3", "NH4", "SO4", "Cl", "PO4", "DOC", "Al", "Si", "H+", "pH", "R", "HR"), "latex", escape = FALSE) %>%
  t(.)%>% kable_styling(latex_options = c("striped", "scale_down", "hold_position")) %>% 
    kable_classic(full_width = F, html_font = "Times") %>% add_header_above(c(" "=2,  "$\\\\u$mol/L"=16))
```

```{r, echo=FALSE, message=FALSE}
##Average 2005-2006 per layer

Reliable_Table<-SS_Reliable_Avg %>% ungroup(Month) %>% group_by(group_id) %>% summarise(across(Ca:HR, ~ mean(.x, na.rm = TRUE)))

#Change pH average (else it won't make sense!)
Reliable_Table$pH = -log(Reliable_Table$H*10^-6, 10)

Reliable_Table %>% mutate_if(is.numeric, format, digits=3,nsmall = 0) %>%
  kbl(caption = "Average Soil Solution Concentrations of Reliable Months (2005-2006)", col.names=c("Soil Layer", "Ca", "Mg", "K", "Na", "NO3", "NH4", "SO4", "Cl", "PO4", "DOC", "Al", "Si", "H+", "pH", "R", "HR"), align = "l", format="latex", booktabs = TRUE, escape = FALSE) %>%t(.)%>% kable_styling(latex_options = c("striped", "scale_down", "hold_position")) %>%
    kable_classic(full_width = F, html_font = "Times") %>% add_header_above(c(" "=1,  "$\\\\mu$mol/L"=16), escape=FALSE)
```

<br>


```{r, echo=FALSE, fig.cap="Monthly Calcium Concentrations by Soil Layer", figures-side, fig.show="hold", out.width="50%", message=FALSE, fig.ncol=2}

Ca_L1<-Ca_SS_L1(Cal_Pretable_SS)
Ca_L1

Ca_L2<-Ca_SS_L2(Cal_Pretable_SS)
Ca_L2


```
```{r, echo=FALSE, fig.cap="Monthly Magnesium Concentrations by Soil Layer", fig.show="hold", out.width="50%"}
Mg_L1<-Mg_SS_L1(Cal_Pretable_SS)
Mg_L1

Mg_L2<-Mg_SS_L2(Cal_Pretable_SS)
Mg_L2
```
```{r, echo=FALSE, fig.cap="Monthly Potassium Concentrations by Soil Layer", fig.show="hold", out.width="50%"}


K_L1<-K_SS_L1(Cal_Pretable_SS)
K_L1

K_L2<-K_SS_L2(Cal_Pretable_SS)
K_L2

```
```{r, echo=FALSE, fig.cap="Monthly Sodium Concentrations by Soil Layer", fig.show="hold", out.width="50%"}


Na_L1<-Na_SS_L1(Cal_Pretable_SS)
Na_L1

Na_L2<-Na_SS_L2(Cal_Pretable_SS)
Na_L2


```
```{r, echo=FALSE, fig.cap="Monthly Sulfate Concentrations by Soil Layer", fig.show="hold", out.width="50%"}
SO4_L1<-SO4_SS_L1(Cal_Pretable_SS)
SO4_L1

SO4_L2<-SO4_SS_L2(Cal_Pretable_SS)
SO4_L2

```
```{r, echo=FALSE, fig.cap="Monthly Chloride Concentrations by Soil Layer", fig.show="hold", out.width="50%"}
Cl_L1<-Cl_SS_L1(Cal_Pretable_SS)
Cl_L1

Cl_L2<-Cl_SS_L2(Cal_Pretable_SS)
Cl_L2

```



<br><br><br>

```{r, echo=FALSE, fig.cap="Monthly Aluminum Concentrations by Soil Layer", fig.show="hold", out.width="50%"}


Al_L1<-Al_SS_L1(Cal_Pretable_SS)
Al_L1

Al_L2<-Al_SS_L2(Cal_Pretable_SS)
Al_L2

```

<br><br><br>

```{r, echo=FALSE, fig.cap="Monthly SiO2 Concentrations by Soil Layer", fig.show="hold", out.width="50%"}

Si_L1<-Si_SS_L1(Cal_Pretable_SS)
Si_L1

Si_L2<-Si_SS_L2(Cal_Pretable_SS)
Si_L2

```

<br><br><br>

```{r, echo=FALSE, fig.cap="Monthly Organic Acid Base (R-) Concentrations by Soil Layer", fig.show="hold", out.width="50%"}


R_L1<-R_SS_L1(Cal_Pretable_SS)
R_L1

R_L2<-R_SS_L2(Cal_Pretable_SS)
R_L2

```

<br><br><br>

```{r, echo=FALSE, fig.cap="Monthly pH by Soil Layer", fig.show="hold", out.width="50%"}


pH_L1<-pH_SS_L1(Cal_Pretable_SS)
pH_L1

pH_L2<-pH_SS_L2(Cal_Pretable_SS)
pH_L2

```

<br><br><br>

```{r, echo=FALSE, fig.cap="Yearly Ammonium concentration by Soil Layer", fig.show="hold", out.width="50%"}


NH4_L1<-NH4_SS_L1(Cal_Pretable_SS)
NH4_L1

NH4_L2<-NH4_SS_L2(Cal_Pretable_SS)
NH4_L2

```

<br><br><br>

```{r, echo=FALSE, fig.cap="Yearly Nitrate concentration by Soil Layer", fig.show="hold", out.width="50%"}


NO3_L1<-NO3_SS_L1(Cal_Pretable_SS)
NO3_L1

NO3_L2<-NO3_SS_L2(Cal_Pretable_SS)
NO3_L2

```

### Lysimeter Comparisons
<br>

```{r, echo=FALSE, message=FALSE}

LL_Year<-Cal_Pretable_LL %>% group_by(YEAR, group_id) %>% summarise(across(Ca:Si, ~sum(.x, na.rm=FALSE)))

Test_LL<-ggplot(LL_Year, aes(x=YEAR, y=Ca, color=group_id))+geom_line()+labs(x="Year", y="Calcium Leaching by Layer (kg/ha)")
Test_LL

Test_LL<-ggplot(LL_Year, aes(x=YEAR, y=Mg, color=group_id))+geom_line()+labs(x="Year", y="Magnesium Leaching by Layer (kg/ha)")
Test_LL



```


<br>

```{r, echo=FALSE, message=FALSE}

Sim_Lysimeter_Flux<-Cal_Pretable_LL %>% filter(group_id %in% c("2", "8")) %>% group_by(group_id, YEAR) %>% summarise(across(Ca:HR, ~sum(.x, na.rm=TRUE))) %>% select(-H, -pH, -R, -HR) %>% filter (YEAR %in% c("2005", "2006")) %>% rename(Depth="group_id")


Sim_Lysimeter_Flux %>% mutate_if(is.numeric, format, digits=2, nsmall= 0) %>%
  kbl(caption = "Simulated Lysimeter Fluxes by Depth (2005-2006)", format="latex", booktabs=TRUE, escape=FALSE, align="c") %>% t(.) %>% kable_styling(latex_options = c("striped", "scale_down", "HOLD_position")) %>% 
         kable_styling(font_size = 12) %>% kable_classic(full_width = F, html_font = "Times") %>% add_header_above(c(" "=2,  "kg/ha"=12))


```

<br>


### Weathering Results

```{r, echo=FALSE, message=FALSE, fig.show="hold", fig.cap="Calcium Weathering (All Layer)", fig.align="center", out.width="75%"}
Weathering_Ca1<-Ca_W_L1(Cal_Pretable_W)
Weathering_Ca1

```

<br>
```{r, echo=FALSE, fig.show="hold", fig.cap="Magnesium Weathering (All Layer)", fig.align="center", out.width="75%"}
Weathering_Mg1<-Mg_W_L1(Cal_Pretable_W)
Weathering_Mg1
```
<br>

```{r, echo=FALSE, fig.show="hold", fig.cap="Potassium Weathering (All Layer)", fig.align="center", out.width="75%"}

#K Weathering
Weathering_K1<-K_W_L1(Cal_Pretable_W)
Weathering_K1
```

<br>

```{r, echo=FALSE, fig.show="hold", fig.cap="Aluminum Weathering (All Layer)", fig.align="center", out.width="75%"}
Weathering_Al1<-Al_W_L1(Cal_Pretable_W)
Weathering_Al1
```

<br>

```{r, echo=FALSE, fig.show="hold", fig.cap="Phosphate Weathering (All Layer)", fig.align="center", out.width="75%"}
Weathering_P1<-P_W_L1(Cal_Pretable_W)
Weathering_P1
```

<br>

```{r, echo=FALSE, fig.show="hold", fig.cap="Silica Weathering (All Layer)", fig.align="center", out.width="75%"}
Weathering_Si1<-Si_W_L1(Cal_Pretable_W)
Weathering_Si1
```

<br>

```{r, echo=FALSE, fig.show="hold", fig.cap="Sodium Weathering (All Layer)", fig.align="center", out.width="75%"}
Weathering_Na1<-Na_W_L1(Cal_Pretable_W)
Weathering_Na1

```



<br><br><br>

### Litter Pool Results

<br>

```{r, echo=FALSE, fig.cap="Forest Floor (O-Layer) Carbon Content Over Simulation Period", fig.show="hold", out.width="50%", fig.subcap=c("Total forest floor carbon content (kg/ha)", "Carbon content of coarse litter (kg/ha)"), fig.ncol=2}

##Should add specific fraction over time as well. 

Litter_C_All<-Litter_Graph(Litter_Pretable$C)
Litter_C_All+labs(y="C (kg/ha)")

Litter_CR<-Litter_Graph(Litter_Pretable$C_CL)
Litter_CR+labs(y="C (kg/ha)")
```
<br>

Looking at a range of soil carbon studies in Douglas-fir forests of the Pacific Northwest, forest floor (defined as non-mineral OM) C content goes from a lower bound of 3,700 kg C/ha in a 9-yr old stand[@cromackSoilCarbonNutrients1999] to 8200 kg C/ha in an average 38 year old stand [edmondsRelationshipsSoilOrganic1994]. These stands were notably N rich compared to the site simulated for the low N site, the soil C should be lower in the simulations as there is about half as much soil N in the low N simulated site as in the sites described in [edmondsRelationshipsSoilOrganic1994]. The high N site has about 21,000 kg N/ha at 1m depth, so it should be modeled to be at the higher end of organic and litter C buildup.  



```{r, echo=FALSE, fig.cap="Forest Floor (O-Layer) Carbon Content Over Simulation Period", fig.show="hold", out.width="50%", fig.subcap=c("Carbon content of fine litter (kg/ha)", "Carbon content of humic litter (kg/ha)"), fig.ncol=2}

##Should add specific fraction over time as well. 

Litter_C_F<-Litter_Graph(Litter_Pretable$C_F)
Litter_C_F+labs(y="C (kg/ha)")

Litter_H<-Litter_Graph(Litter_Pretable$C_H)
Litter_H+labs(y="C (kg/ha)")
```

<br>

Note that the fine litter pool (the stage between humus and fresh/coarse litter) is growing in this model. This might deviate from observed behavior. 

<br>

```{r, echo=FALSE, message=FALSE, fig.show="hold", out.width="50%", fig.cap="Forest Floor/O-horizon Ca content over time (a). and net annual Ca return in litterfall (b).", fig.subcap=c("Ca Content in each litter decomposition stage (kg/ha)", "Ca net annual return in litterfall (kg/ha)")}

Ca_OH_All<-ggplot(Litter_Pretable, aes(x=Date))+geom_line(mapping=aes(y=Ca_CL, color="Coarse Litter"))+geom_line(mapping=aes(y=Ca_F, color="Fine Litter"))+geom_line(mapping=aes(y=Ca_H, color="Humic Litter"))+
  geom_line(mapping= aes(y=Ca, color="Total Litter"))+
  labs(y="Ca (kg/ha)", color="Litter Type")

Ca_OH_All

#Mutate Litter_Fall so it's on a yearly time step; can't use the flux data because it is unfortunately specified far below this code 

Litter_Fall_Year<-Litter_Fall %>% group_by(Year) %>% summarise(across(N:P, ~sum(.x, na.rm= TRUE)))

Ca_LF.G<-ggplot(Litter_Fall_Year, aes(x=Year, y=Ca, color="Ca Litterfall Return"))+geom_line()
Ca_LF.G+theme(legend.title = element_blank())

```
<br>

### Soil Organic Matter Results

```{r, echo=FALSE, message=FALSE, fig.show="hold"}
SOM<-SOM %>%group_by(Year, group_id)%>% summarize(across(C:S, ~mean(.x, na.rm = TRUE)))

SOM_C<-ggplot(SOM, aes(x=Year, y=C,color=group_id))+geom_line()
SOM_C

```

<br>

Mineral soil SOM C content is very high compared to other pools of carbon in the ecosystem, soil carbon should buildup over time assuming available surfaces exist for soil carbon "stabilization". In NutsFor, the SOM pool is represented by an active microbial pool, so there are issues with building up SOM in the soil as one might expect from a real stand. Microbial growth is limited by soil moisture and nutrient availability like the tree pool, so it is not a wholly adequate representation of C stabilization. Instead of calibrating this output to show buildup, I calibrated it such that it was "level", thus, soil carbon additions to the mineral soil are dictated by DOC percolation with water flow.  


```{r, echo=FALSE, message=FALSE, fig.show="hold", out.width="50%", fig.cap="Forest Floor/O-horizon Mg content over time (a). and net annual Mg return in litterfall (b).", fig.subcap=c("Mg Content in each litter decomposition stage (kg/ha)", "Mg net annual return in litterfall (kg/ha)")}

Mg_OH_All<-ggplot(Litter_Pretable, aes(x=Date))+geom_line(mapping=aes(y=Mg_CL, color="Coarse Litter"))+geom_line(mapping=aes(y=Mg_F, color="Fine Litter"))+geom_line(mapping=aes(y=Mg_H, color="Humic Litter"))+
  geom_line(mapping= aes(y=Mg, color="Total Litter"))+
  labs(y="Mg (kg/ha)", color="Litter Type")

Mg_OH_All

#Mutate Litter_Fall so it's on a yearly time step; can't use the flux data because it is unfortunately specified far below this code 

Litter_Fall_Year<-Litter_Fall %>% group_by(Year) %>% summarise(across(N:P, ~sum(.x, na.rm= TRUE)))

Mg_LF.G<-ggplot(Litter_Fall_Year, aes(x=Year, y=Mg, color="Mg Litterfall Return"))+geom_line()
Mg_LF.G+theme(legend.title = element_blank())

```

<br>


```{r, echo=FALSE, message=FALSE, fig.show="hold", out.width="50%", fig.cap="Forest Floor/O-horizon K content over time (a). and net annual K return in litterfall (b).", fig.subcap=c("K Content in each litter decomposition stage (kg/ha)", "K net annual return in litterfall (kg/ha)")}

K_OH_All<-ggplot(Litter_Pretable, aes(x=Date))+geom_line(mapping=aes(y=K_CL, color="Coarse Litter"))+geom_line(mapping=aes(y=K_F, color="Fine Litter"))+geom_line(mapping=aes(y=K_H, color="Humic Litter"))+
  geom_line(mapping= aes(y=K, color="Total Litter"))+
  labs(y="K (kg/ha)", color="Litter Type")

K_OH_All

#Mutate Litter_Fall so it's on a yearly time step; can't use the flux data because it is unfortunately specified far below this code 

Litter_Fall_Year<-Litter_Fall %>% group_by(Year) %>% summarise(across(N:P, ~sum(.x, na.rm= TRUE)))

K_LF.G<-ggplot(Litter_Fall_Year, aes(x=Year, y=K, color="K Litterfall Return"))+geom_line()
K_LF.G+theme(legend.title = element_blank())

```

<br>

```{r, echo=FALSE, message=FALSE, fig.show="hold", out.width="50%", fig.cap="Forest Floor/O-horizon S content over time (a). and net annual S return in litterfall (b).", fig.subcap=c("S Content in each litter decomposition stage (kg/ha)", "S net annual return in litterfall (kg/ha)")}

S_OH_All<-ggplot(Litter_Pretable, aes(x=Date))+geom_line(mapping=aes(y=S_CL, color="Coarse Litter"))+geom_line(mapping=aes(y=S_F, color="Fine Litter"))+geom_line(mapping=aes(y=S_H, color="Humic Litter"))+
  geom_line(mapping= aes(y=S, color="Total Litter"))+
  labs(y="S (kg/ha)", color="Litter Type")

S_OH_All

#Mutate Litter_Fall so it's on a yearly time step; can't use the flux data because it is unfortunately specified far below this code 

Litter_Fall_Year<-Litter_Fall %>% group_by(Year) %>% summarise(across(N:P, ~sum(.x, na.rm= TRUE)))

S_LF.G<-ggplot(Litter_Fall_Year, aes(x=Year, y=S, color="S Litterfall Return"))+geom_line()
S_LF.G+theme(legend.title = element_blank())

```

<br>

```{r, echo=FALSE, message=FALSE, fig.show="hold", out.width="50%", fig.cap="Forest Floor/O-horizon P content over time (a). and net annual P return in litterfall (b).", fig.subcap=c("P Content in each litter decomposition stage (kg/ha)", "P net annual return in litterfall (kg/ha)")}

P_OH_All<-ggplot(Litter_Pretable, aes(x=Date))+geom_line(mapping=aes(y=P_CL, color="Coarse Litter"))+geom_line(mapping=aes(y=P_F, color="Fine Litter"))+geom_line(mapping=aes(y=P_H, color="Humic Litter"))+
  geom_line(mapping= aes(y=P, color="Total Litter"))+
  labs(y="P (kg/ha)", color="Litter Type")

P_OH_All

#Mutate Litter_Fall so it's on a yearly time step; can't use the flux data because it is unfortunately specified far below this code 

Litter_Fall_Year<-Litter_Fall %>% group_by(Year) %>% summarise(across(N:P, ~sum(.x, na.rm= TRUE)))

P_LF.G<-ggplot(Litter_Fall_Year, aes(x=Year, y=P, color="P Litterfall Return"))+geom_line()
P_LF.G+theme(legend.title = element_blank())

```

<br>

```{r, echo=FALSE, message=FALSE, fig.show="hold", out.width="50%", fig.cap="Forest Floor/O-horizon N content over time (a). and net annual N return in litterfall (b).", fig.subcap=c("N Content in each litter decomposition stage (kg/ha)", "N net annual return in litterfall (kg/ha)")}

N_OH_All<-ggplot(Litter_Pretable, aes(x=Date))+geom_line(mapping=aes(y=N_CL, color="Coarse Litter"))+geom_line(mapping=aes(y=N_F, color="Fine Litter"))+geom_line(mapping=aes(y=N_H, color="Humic Litter"))+
  geom_line(mapping= aes(y=N, color="Total Litter"))+
  labs(y="N (kg/ha)", color="Litter Type")

N_OH_All

#Mutate Litter_Fall so it's on a yearly time step; can't use the flux data because it is unfortunately specified far below this code 

Litter_Fall_Year<-Litter_Fall %>% group_by(Year) %>% summarise(across(N:N, ~sum(.x, na.rm= TRUE)))

N_LF.G<-ggplot(Litter_Fall_Year, aes(x=Year, y=N, color="N Litterfall Return"))+geom_line()
N_LF.G+theme(legend.title = element_blank())

```

<br>



### Tree Nutrient Content
<br>

```{r, echo=FALSE, message=FALSE, fig.cap="Base Cation Nutrient Content in Simulated Forest", fig.align='center', out.width="50%", fig.show="hold", fig.ncol=2, fig.subcap=c('Calcium content in each biomass compartment', 'Magnesium content in each biomass compartment', 'Potassium content in each biomass compartment')}

#By doing selection here, we allow for 1 file to be read from rather than multiple. 

#Ca

Tree_Nut_Ca<-Tree_Nut_All %>% select(Ca_F, Ca_Bol, Ca_Brh, Ca_Brk, YEAR, Month)

Tree_Nut_Ca<-Tree_Nut_Ca %>% mutate(Date= make_date(YEAR, Month)) %>% select (-YEAR, -Month) %>% group_by(Date)

Tree_Nut_Ca_Melt<-Tree_Nut_Ca_Melt<-melt(Tree_Nut_Ca, id.vars= c("Date"))

Ca_Nut<-ggplot(Tree_Nut_Ca_Melt, aes(x=Date, y=value, fill=variable))+geom_area()+labs(y="Ca Content in Biomass: kg/ha")+ scale_fill_discrete(name="Biomass Compartment", labels=c("Foliage", "Bole", "Branch", "Bark"))
Ca_Nut

#Mg
Tree_Nut_Mg<-Tree_Nut_All %>% select(Mg_F, Mg_Bol, Mg_Brh, Mg_Brk, YEAR, Month)

Tree_Nut_Mg<-Tree_Nut_Mg %>% mutate(Date= make_date(YEAR, Month)) %>% select (-YEAR, -Month) %>% group_by(Date)

Tree_Nut_Mg_Melt<-Tree_Nut_Mg_Melt<-melt(Tree_Nut_Mg, id.vars= c("Date"))

Mg_Nut<-ggplot(Tree_Nut_Mg_Melt, aes(x=Date, y=value, fill=variable))+geom_area()+labs(y="Mg Content in Biomass: kg/ha")+ scale_fill_discrete(name="Biomass Compartment", labels=c("Foliage", "Bole", "Branch", "Bark"))
Mg_Nut


#K

Tree_Nut_K<-Tree_Nut_All %>% select(K_F, K_Bol, K_Brh, K_Brk, YEAR, Month)

Tree_Nut_K<-Tree_Nut_K %>% mutate(Date= make_date(YEAR, Month)) %>% select (-YEAR, -Month) %>% group_by(Date)

Tree_Nut_K_Melt<-Tree_Nut_K_Melt<-melt(Tree_Nut_K, id.vars= c("Date"))

K_Nut<-ggplot(Tree_Nut_K_Melt, aes(x=Date, y=value, fill=variable))+geom_area()+labs(y="K Content in Biomass: kg/ha")+ scale_fill_discrete(name="Biomass Compartment", labels=c("Foliage", "Bole", "Branch", "Bark"))
K_Nut

```
<br>
```{r, echo=FALSE, message=FALSE, fig.cap="N, S, and P Nutrient Contents and biomass per compartment", fig.align='center', out.width="50%", fig.show="hold", fig.ncol=2, fig.subcap=c('Nitrogen content in each biomass compartment', 'Sulfur content in each biomass compartment', 'Phosphorous content in each biomass compartment', 'Biomass of each compartment')}

#N

Tree_Nut_N<-Tree_Nut_All %>% select(N_F, N_Bol, N_Brk, YEAR, Month, N_Brh)

Tree_Nut_N<-Tree_Nut_N %>% mutate(Date= make_date(YEAR, Month)) %>% select (-YEAR, -Month) %>% group_by(Date)

Tree_Nut_N_Melt<-Tree_Nut_N_Melt<-melt(Tree_Nut_N, id.vars= c("Date"))

N_Nut<-ggplot(Tree_Nut_N_Melt, aes(x=Date, y=value, fill=variable))+geom_area()+labs(y="N Content in Biomass: kg/ha")+ scale_fill_discrete(name="Biomass Compartment", labels=c("Foliage", "Bole", "Branch", "Bark"))
N_Nut

#S
Tree_Nut_S<-Tree_Nut_All %>% select(S_F, S_Bol, S_Brh, S_Brk, YEAR, Month)

Tree_Nut_S<-Tree_Nut_S %>% mutate(Date= make_date(YEAR, Month)) %>% select (-YEAR, -Month) %>% group_by(Date)

Tree_Nut_S_Melt<-Tree_Nut_S_Melt<-melt(Tree_Nut_S, id.vars= c("Date"))

S_Nut<-ggplot(Tree_Nut_S_Melt, aes(x=Date, y=value, fill=variable))+geom_area()+labs(y="S Content in Biomass: kg/ha")+ scale_fill_discrete(name="Biomass Compartment", labels=c("Foliage", "Bole", "Branch", "Bark"))
S_Nut

#P
Tree_Nut_P<-Tree_Nut_All %>% select(P_F, P_Bol, P_Brh, P_Brk, YEAR, Month)

Tree_Nut_P<-Tree_Nut_P %>% mutate(Date= make_date(YEAR, Month)) %>% select (-YEAR, -Month) %>% group_by(Date)

Tree_Nut_P_Melt<-Tree_Nut_P_Melt<-melt(Tree_Nut_P, id.vars= c("Date"))

Tree_Nut_P_Melt$value<-as.numeric(Tree_Nut_P_Melt$value)

P_Nut<-ggplot(Tree_Nut_P_Melt, aes(x=Date, y=value, fill=variable))+geom_area()+labs(y="P Content in Biomass: kg/ha")+ scale_fill_discrete(name="Biomass Compartment", labels=c("Foliage", "Bole", "Branch", "Bark"))
P_Nut

#Dry Weight/Biomass

Tree_Nut_DW<-Tree_Nut_All %>% select(DW_F, DW_Bol, DW_Brh, DW_Brk, YEAR, Month)

Tree_Nut_DW<-Tree_Nut_DW %>% mutate(Date= make_date(YEAR, Month)) %>% select (-YEAR, -Month) %>% group_by(Date)

Tree_Nut_DW_Melt<-Tree_Nut_DW_Melt<-melt(Tree_Nut_DW, id.vars= c("Date"))

DW_Nut<-ggplot(Tree_Nut_DW_Melt, aes(x=Date, y=value, fill=variable))+geom_area()+labs(y="Dry Weight of Biomass Compartments: kg/ha")+ scale_fill_discrete(name="Biomass Compartment", labels=c("Foliage", "Bole", "Branch", "Bark"))
DW_Nut
```

<br>

### Analysis 1: Stack Flux Data

```{r, echo=FALSE, message=FALSE}
#Final Mutation for Analysis 1, must be done AFTER leaching_table_1m is assigned. 

Leaching_Table_Graphable<-Tab_Func_LL_Yr(Cal_Pretable_LL)
Leaching_Table_1m<-Leaching_Table_Graphable %>% filter(group_id %in% c(8))

Analysis_Bound<- cbind(Leaching_Table_1m, Analysis_1)

Analysis_1_Ready<-Analysis_Bound %>% group_by(V1) %>% 
    mutate(Ca_Net=Ca_Wet+Ca_WTH+Ca_L_Min+Ca_SOM_Min-Ca_TU-Ca) %>%
    mutate(Mg_Net=Mg_Wet+Mg_WTH+Mg_L_Min+Mg_SOM_Min-Mg_TU-Mg) %>% 
    mutate(K_Net=K_Wet+K_WTH+K_L_Min+K_SOM_Min-K_TU-K+K_Folx) %>%
    mutate(SO4_Net=SO4_Wet+ S_L_Min+S_SOM_Min-S_TU-SO4) %>%
    mutate(N_Net=Ntot_Wet+ N_L_Min+N_SOM_Min-N_TU-SO4) %>%
    mutate(P_Net=P_WTH+ P_L_Min+P_SOM_Min-P_TU-P)

```


<br>


```{r, echo=FALSE, out.width="50%", fig.ncol=2, fig.show="hold", message=FALSE, fig.cap="Calcium input and output comparison graphs", fig.subcap=c("Ca input and output fluxes over time", "Total Average Ca input and output fluxes")}

#Make sure to define leaching table 1m before
Analysis_Bound<-Analysis_Bound %>% ungroup(YEAR) %>% select(-YEAR)

Ca_Flux<-Analysis_Bound %>% select (Ca, Ca_Wet, Ca_WTH, Ca_TU, Year, Ca_LF, Ca_L_Min)
Ca_Flux$Ca_LF<-Ca_Flux$Ca_LF*10

Ca_Melt<-melt(Ca_Flux, id.vars = c("Year") )

Ca_Stacked<-ggplot(Ca_Melt, aes(x=Year, y=value, fill=variable))+geom_area()+labs(y="Ca Flux From Ecosystem Pools: kg/ha/yr")+
   scale_fill_discrete(name = "Legend", labels = c("Leaching Flux", "Deposition", "Weathering Flux", "Total ", "Litterfall Return", "Litter Mineralization"))
Ca_Stacked


Ca_Forged<-dcast(Ca_Melt, Year~variable)

Ca_Forged_Mean<-Ca_Forged %>% summarise(across(Ca:Ca_L_Min, ~mean(.x, na.rm=TRUE)))

Ca_ReForged_Mean<-melt(Ca_Forged_Mean)

Bar_Ca<-ggplot(Ca_ReForged_Mean, aes(fill=variable, y=value, x="HN BAS Base Case")) + 
    geom_bar(position="stack", stat="identity")+
   scale_fill_discrete(name = "Average Ca Fluxes", labels = c("Leaching Flux", "Deposition", "Weathering Flux", "Total ", "Litterfall Return", "Litter Mineralization"))+
  labs(x="Site", y=expression(Ca~kg~'*'~(ha~'*'~yr)^-1))

Bar_Ca



```

<br>

```{r, echo=FALSE, out.width="50%", fig.ncol=2, fig.show="hold", message=FALSE, fig.cap="Magnesium input and output comparison graphs", fig.subcap=c("Mg input and output fluxes over time", "Total Average Mg input and output fluxes")}

Mg_Flux<-Analysis_Bound %>% select (Mg, Mg_Wet, Mg_WTH, Mg_TU, Year, Mg_LF, Mg_L_Min)
Mg_Flux$Mg_LF<-Mg_Flux$Mg_LF*10

Mg_Melt<-melt(Mg_Flux, id.vars = c("Year") )

Mg_Stacked<-ggplot(Mg_Melt, aes(x=Year, y=value, fill=variable))+geom_area()+labs(y="Mg Flux From Ecosystem Pools: kg/ha/yr")+
   scale_fill_discrete(name = "Legend", labels = c("Leaching Flux", "Deposition", "Weathering Flux", "Total ", "Litterfall Return", "Litter Mineralization"))
Mg_Stacked

Mg_Forged<-dcast(Mg_Melt, Year~variable)

Mg_Forged_Mean<-Mg_Forged %>% summarise(across(Mg:Mg_L_Min, ~mean(.x, na.rm=TRUE)))

Mg_ReForged_Mean<-melt(Mg_Forged_Mean)

Bar_Mg<-ggplot(Mg_ReForged_Mean, aes(fill=variable, y=value, x="HN BAS Base Case")) + 
    geom_bar(position="stack", stat="identity")+
   scale_fill_discrete(name = "Average Mg Fluxes", labels = c("Leaching Flux", "Deposition", "Weathering Flux", "Total ", "Litterfall Return", "Litter Mineralization"))+
  labs(x="Site", y=expression(Mg~kg~'*'~(ha~'*'~yr)^-1))

Bar_Mg




```

<br>

```{r, echo=FALSE, out.width="50%", fig.ncol=2, fig.show="hold", message=FALSE, fig.cap="Potassium input and output comparison graphs", fig.subcap=c("K input and output fluxes over time", "Total Average K input and output fluxes")}

K_Flux<-Analysis_Bound %>% select (K, K_Wet, K_WTH, K_TU, Year, K_LF, K_L_Min)
K_Flux$K_LF<-K_Flux$K_LF*10

K_Melt<-melt(K_Flux, id.vars = c("Year") )

K_Stacked<-ggplot(K_Melt, aes(x=Year, y=value, fill=variable))+geom_area()+labs(y="K Flux From Ecosystem Pools: kg/ha/yr")+
   scale_fill_discrete(name = "Legend", labels = c("Leaching Flux", "Deposition", "Weathering Flux", "Total ", "Litterfall Return", "Litter Mineralization"))
K_Stacked

K_Forged<-dcast(K_Melt, Year~variable)

K_Forged_Mean<-K_Forged %>% summarise(across(K:K_L_Min, ~mean(.x, na.rm=TRUE)))

K_ReForged_Mean<-melt(K_Forged_Mean)

Bar_K<-ggplot(K_ReForged_Mean, aes(fill=variable, y=value, x="HN BAS Base Case")) + 
    geom_bar(position="stack", stat="identity")+
   scale_fill_discrete(name = "Average K Fluxes", labels = c("Leaching Flux", "Deposition", "Weathering Flux", "Total ", "Litterfall Return", "Litter Mineralization"))+
  labs(x="Site", y=expression(K~kg~'*'~(ha~'*'~yr)^-1))

Bar_K
```

<br>

```{r, fig.show="hold", echo=FALSE, out.width="50%", echo=FALSE, message=FALSE, fig.cap="Sulfur input and output comparison graphs", fig.subcap=c("S input and output fluxes over time", "Total Average S input and output fluxes")}

SO4_Flux<-Analysis_Bound %>% select (SO4, SO4_Wet, S_TU, Year, S_LF, S_L_Min)
SO4_Flux$S_LF<-SO4_Flux$S_LF*10

SO4_Melt<-melt(SO4_Flux, id.vars = c("Year") )


SO4_Stacked<-ggplot(SO4_Melt, aes(x=Year, y=value, fill=variable))+geom_area()+labs(y="SO4-S Flux From Ecosystem Pools:kg/ha/yr")+
  scale_fill_discrete(name = "Legend", labels = c("Leaching Flux", "Deposition", "Total ", "Litterfall Return", "Litter Mineralization"))
SO4_Stacked

SO4_Forged<-dcast(SO4_Melt, Year~variable)

SO4_Forged_Mean<-SO4_Forged %>% summarise(across(SO4:S_L_Min, ~mean(.x, na.rm=TRUE)))

SO4_ReForged_Mean<-melt(SO4_Forged_Mean)

Bar_SO4<-ggplot(SO4_ReForged_Mean, aes(fill=variable, y=value, x="HN BAS Base Case")) + 
    geom_bar(position="stack", stat="identity")+
   scale_fill_discrete(name = "Average SO4-S Fluxes", labels = c("Leaching Flux", "Deposition", "Total ", "Litterfall Return", "Litter Mineralization"))+
  labs(x="Site", y=expression(SO4~kg~'*'~(ha~'*'~yr)^-1))

Bar_SO4


```

The sulfate adsorbed pool depletes itself, the organic sulfur pool becomes increasingly dominant. This behavior is not unreasonable, however I would expect higher sulfate adsorption.

<br>

```{r, fig.show="hold", out.width="50%", echo=FALSE, message=FALSE, fig.cap="Nitrogen input and output comparison graphs", fig.subcap=c("N input and output fluxes over time", "Total Average N input and output fluxes")}


N_Flux<-Analysis_Bound %>% select (NO3, NH4, Ntot_Wet, N_TU, Year, N_LF, N_L_Min, N_SOM_Min)
N_Flux$LL<-N_Flux$NO3+N_Flux$NH4
N_Flux$N_LF<-N_Flux$N_LF*10

N_Flux<-N_Flux %>% select(-NO3, -NH4)

N_Melt<-melt(N_Flux, id.vars = c("Year"))

N_Stacked<-ggplot(N_Melt, aes(x=Year, y=value, fill=variable))+geom_area()+labs(y="N Flux From Ecosystem Pools: kg/ha/yr")+
   scale_fill_discrete(name = "Legend", labels = c("Deposition", "Total ", "Litterfall Return", "Litter Mineralization", "SOM Mineralization", "Leaching Loss"))
N_Stacked

N_Forged<-dcast(N_Melt, Year~variable)

N_Forged_Mean<-N_Forged %>% summarise(across(Ntot_Wet:LL, ~mean(.x, na.rm=TRUE)))

N_ReForged_Mean<-melt(N_Forged_Mean)

Bar_N<-ggplot(N_ReForged_Mean, aes(fill=variable, y=value, x="HN BAS Base Case")) + 
    geom_bar(position="stack", stat="identity")+
   scale_fill_discrete(name = "Average N Fluxes", labels = c("Deposition", "Total ", "Litterfall Return", "Litter Mineralization", "SOM Mineralization", "Leaching Loss"))+
  labs(x="Site", y=expression(N~kg~'*'~(ha~'*'~yr)^-1))

Bar_N
```

There looks to be a SOM reporting bug which causes a large negative spike in N mineralization, it does not seem to affect the simulation in terms of N flux or nutrient , which tells me it is likely a reporting error. 

### Cation Exchange Capacity
```{r, echo=FALSE, out.width="50%", fig.ncol=2, fig.show="hold", message=FALSE, fig.cap="Calcium and Magnesium on exchangerover time", fig.subcup=c("Ca adsorption (kg/ha)", "Mg adsorption (kg/ha)")}

CEC_All$Date<-as.Date(CEC_All$Date)

CEC_Ca<-CEC_Grapher(CEC_All$Ca)
CEC_Ca+labs(y="Ca on cation exchange surfaces (kg/ha)")+ scale_x_discrete(guide = guide_axis(check.overlap = TRUE))+ scale_x_date(date_labels = "%Y")+scale_fill_discrete(name="Layer Number")

CEC_Mg<-CEC_Grapher(CEC_All$Mg)
CEC_Mg+labs(y="Mg on cation exchange surfaces (kg/ha)")+ scale_x_discrete(guide = guide_axis(check.overlap = TRUE))+ scale_x_date(date_labels = "%Y")+scale_fill_discrete(name="Layer Number")


```

<br>

```{r, echo=FALSE, out.width="50%", fig.ncol=2, fig.show="hold", message=FALSE,fig.cap="Potassium and Sodium on exchangerover time", fig.subcup=c("K adsorption (kg/ha)", "Na adsorption (kg/ha)")}

CEC_K<-CEC_Grapher(CEC_All$K)
CEC_K+labs(y="K on cation exchange surfaces (kg/ha)")+ scale_x_discrete(guide = guide_axis(check.overlap = TRUE))+ scale_x_date(date_labels = "%Y")+scale_fill_discrete(name="Layer Number")

CEC_Na<-CEC_Grapher(CEC_All$Na)
CEC_Na+labs(y="Na on cation exchange surfaces (kg/ha)")+ scale_x_discrete(guide = guide_axis(check.overlap = TRUE))+ scale_x_date(date_labels = "%Y")+scale_fill_discrete(name="Layer Number")

```

<br>

```{r, echo=FALSE, out.width="50%", fig.ncol=2, fig.show="hold", message=FALSE, fig.cap="Ammonium and Aluminum on exchangerover time", fig.subcup=c("NH4 adsorption (kg/ha)", "Al adsorption (kg/ha)")}


CEC_NH4<-CEC_Grapher(CEC_All$NH4)
CEC_NH4+labs(y="NH4 on cation exchange surfaces (kg/ha)")+ scale_x_discrete(guide = guide_axis(check.overlap = TRUE))+ scale_x_date(date_labels = "%Y")+scale_fill_discrete(name="Layer Number")

CEC_Al<-CEC_Grapher(CEC_All$Al)
CEC_Al+labs(y="Al on cation exchange surfaces (kg/ha)")+ scale_x_discrete(guide = guide_axis(check.overlap = TRUE))+ scale_x_date(date_labels = "%Y")+scale_fill_discrete(name="Layer Number")

```

<br><br><br>

### Anion Exchange Capacity 


```{r, echo=FALSE, message=FALSE, message=FALSE}


AEC_All$group_id<-as.factor(AEC_All$group_id)
AEC_All$Date<-as.Date(AEC_All$Date)

SO4_AEC<-AEC_Grapher(AEC_All$SO4)
SO4_AEC+labs(y="Soil adsorbed Sulfate (SO4-S kg/ha)")+scale_x_discrete(guide = guide_axis(check.overlap = TRUE))+scale_x_date(date_labels = "%Y")+scale_fill_discrete(name="Layer Number")


PO4_AEC<-AEC_Grapher(AEC_All$PO4)
PO4_AEC+labs(y="Soil adsorbed PO4-P (kg/ha)")+scale_x_discrete(guide = guide_axis(check.overlap = TRUE))+scale_x_date(date_labels = "%Y")+scale_fill_discrete(name="Layer Number")

Cl_AEC<-AEC_Grapher(AEC_All$Cl)

Cl_AEC+labs(y="Soil adsorbed Chloride kg/ha)")+scale_x_discrete(guide = guide_axis(check.overlap = TRUE))+scale_x_date(date_labels = "%Y")+scale_fill_discrete(name="Layer Number")

```

<br>

The phosphate adsorption is set from the original parameterization I received from Gregory. It tends to build up, which implies a high soil solution concentration (adsorption is determined by concentration).

Sulfate adsorption is weak and drains easily, I set a low adsorbed sulfate pool following IFS data from the Thompson site (glacial outwash, inceptisol). According to the book *Atmospheric Sulfur Deposition: Environmental and Health Impacts*, sulfur is mostly locked in organic compartments rather than on the adsorption surfaces. We might expect that sulfate, like phosphate, would increase on the AEC, however the input of sulfate relative to the adsorption and  of sulfate is likely too low to facilitate adsorption. This is well supported by IFS data that show low sulfate adsorption on potentially high capacity adsorbing soils. The higher sulfate concentrations observed at the high N site could well be due to a higher inherent sulfur pool, possibly a condition of higher sulfate-mineral weathering, or due to a competitive response with phosphate.  


<br>

### Other 

<br>

```{r, echo=FALSE, message=FALSE}

Litter_Fall$Dry.weight_kgha<-Litter_Fall$Dry.weight*10

Litter_Fall[c(11:16)]<-lapply(Litter_Fall[c(11:16)], as.numeric)

Litter_Fall<-Litter_Fall %>% group_by(Year) %>% select(-Date) %>%
  summarise(across(Dry.weight:Dry.weight_kgha, ~sum(.x, na.rm=TRUE)))

LF<-ggplot(Litter_Fall, aes(x=Year, y=Dry.weight_kgha))+geom_line()+labs(y="Litter Fall Dry Weight (kg/ha)")
LF

```

<br>

```{r, echo=FALSE, message=FALSE, out.width="50%", fig.ncol=2, fig.show="hold", message=FALSE, fig.cap="N and P Potential  to Actual  Difference", fig.subcup=c("N  Difference", "P  Difference")}


N_PP<-Plant_Pool_Graph(Plant_Pool$Year, Plant_Pool$N_Diff)
N_PP+labs(x="Year", y=expression(N~Diff.~(mol/m^2)))

P_PP<-Plant_Pool_Graph(Plant_Pool$Year, Plant_Pool$P_Diff)
P_PP+labs(x="Year", y=expression(P~Diff.~(mol/m^2)))


```
<br>

```{r, echo=FALSE, message=FALSE, out.width="50%", fig.ncol=2, fig.show="hold", message=FALSE, fig.cap="Ca and Mg Potential  to Actual  Difference", fig.subcup=c("Ca  Difference", "Mg  Difference")}


Ca_PP<-Plant_Pool_Graph(Plant_Pool$Year, Plant_Pool$Ca_Diff)
Ca_PP+labs(x="Year", y=expression(Ca~Diff.~(mol/m^2)))

Mg_PP<-Plant_Pool_Graph(Plant_Pool$Year, Plant_Pool$Mg_Diff)
Mg_PP+labs(x="Year", y=expression(Mg~Diff.~(mol/m^2)))


```
<br>

```{r, echo=FALSE, message=FALSE, out.width="50%", fig.ncol=2, fig.show="hold", message=FALSE, fig.cap="K and S Potential  to Actual  Difference", fig.subcup=c("K  Difference", "S  Difference")}


K_PP<-Plant_Pool_Graph(Plant_Pool$Year, Plant_Pool$K_Diff)
K_PP+labs(x="Year", y=expression(K~Diff.~(mol/m^2)))

S_PP<-Plant_Pool_Graph(Plant_Pool$Year, Plant_Pool$S_Diff)
S_PP+labs(x="Year", y=expression(S~Diff.~(mol/m^2)))


```

What I get from this calculation is that for all nutrients except N and P, the stand is able to extract near exactly the required amount of each nutrient for growth. For K, foliar leaching causes excessive total , however the mineral pool is rich enough in K to facilitate this excess . These graphs do not take into consideration that  can vary by 20% before growth limitation is induced. 