---
title: 'Calibration Report: Low N Basalt Site'
author: "Kaveh Gholamhossein Siah"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  pdf_document:
    toc: yes
    toc_depth: 3
    extra_dependencies: "subfig"
    
geometry: margin=2 cm
fig_caption: yes
---
<br><br><br>

```{r global_options, include=FALSE, message=FALSE}
#This global option holds figures in the correct place (stops floating in pdf)
knitr::opts_chunk$set(fig.pos = 'H')

```


```{r, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
library(kableExtra)
library(ggplot2)
library(dplyr)
library(captioner)
library(car)
library(janitor)
library(scales)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}

source("~/Project_Master/Test_Rep/Code/LN_BAS/Weathering_LN_BAS_Mutator.R")

source("~/Project_Master/Test_Rep/Code/LN_BAS/Soil_Soln_LN_BAS_Mutator.R")

source("~/Project_Master/Test_Rep/Code/LN_BAS/Litter_Pool_LN_BAS_Mutator.R")

source("~/Project_Master/Test_Rep/Code/LN_BAS/TreeNut_LN_BAS_Mutator.R")

source("~/Project_Master/Test_Rep/Code/LN_BAS/Analysis_1_Mutator.R")



                                    ##Load Data, edit data as needed##
#umol/L
Cal_Pretable_Parent<-read.csv2("~/Project_Master/Test_Rep/Output/Calibration/Output_LN_BAS/Edited Data/Soil_Solution_All2.csv", header=TRUE)
Cal_Pretable_SS<-Cal_Pretable_Parent %>% filter(group_id %in% c("10", "11", "12", "13", "14", "15", "16", "17"))
Cal_Pretable_SS$group_id<-as.character(Cal_Pretable_SS$group_id)


#Kg/ha
Cal_Pretable_LL<-Cal_Pretable_Parent %>% filter(group_id %in% c("1", "2", "3", "4", "5", "6", "7", "8"))
Cal_Pretable_LL$group_id<-as.character(Cal_Pretable_LL$group_id)


Cal_Pretable_SS_Yr<-Cal_Pretable_SS %>% group_by(group_id, YEAR) %>% summarise(across(Ca:HR, ~mean(.x, na.rm=TRUE)))

Cal_Pretable_W<-read.csv2("~/Project_Master/Test_Rep/Output/Calibration/Output_LN_BAS/Edited Data/Weathering_All.csv", header=TRUE)

Litter_Pretable<-read.csv2("~/Project_Master/Test_Rep/Output/Calibration/Output_LN_BAS/Edited Data/Litter_Pool.csv", header=TRUE)
Litter_Pretable$Date<-as.Date(as.character(Litter_Pretable$Date))

Tree_Bark<-read.csv2("~/Project_Master/Test_Rep/Output/Calibration/Output_LN_BAS/Edited Data/Tree_Bark.csv", header=TRUE)
Tree_Bark$Date<-as.Date(Tree_Bark$Date)

Tree_Wood<-read.csv2("~/Project_Master/Test_Rep/Output/Calibration/Output_LN_BAS/Edited Data/Tree_Wood.csv", header=TRUE)
Tree_Wood$Date<-as.Date(Tree_Wood$Date)

Tree_Branch<-read.csv2("~/Project_Master/Test_Rep/Output/Calibration/Output_LN_BAS/Edited Data/Tree_Branch.csv")
Tree_Branch$Date<-as.Date(Tree_Branch$Date)

Tree_Foliage<-read.csv2("~/Project_Master/Test_Rep/Output/Calibration/Output_LN_BAS/Edited Data/Tree_Foliage.csv")
Tree_Foliage$Date<-as.Date(Tree_Foliage$Date)

Tree_Ligneous<-read.csv2("~/Project_Master/Test_Rep/Output/Calibration/Output_LN_BAS/Edited Data/Tree_Ligneous.csv")
Tree_Ligneous$Date<-as.Date(Tree_Ligneous$Date)


Litter_Fall<-read.csv2("~/Project_Master/Test_Rep/Output/Calibration/Output_LN_BAS/Edited Data/Litter_Fall.csv", header=TRUE)

Analysis_1<-read.csv2("~/Project_Master/Test_Rep/Output/Calibration/Output_LN_BAS/Edited Data/Analysis_1.csv", header=TRUE)



                                            ##Load Functions for Analysis##

source("~/Project_Master/Test_Rep/Code/Functions/Tabulator.R")
source("~/Project_Master/Test_Rep/Code/Functions/Grapher_Cal_Soil_R.R")
source("~/Project_Master/Test_Rep/Code/Functions/Grapher_Cal_Weathering.R")
source("~/Project_Master/Test_Rep/Code/Functions/Grapher_Cal_SOM.R")
source("~/Project_Master/Test_Rep/Code/Functions/Grapher_Litter.R")
source("~/Project_Master/Test_Rep/Code/Functions/Grapher_Bio_Compart.R")
source("~/Project_Master/Test_Rep/Code/Functions/LL_1M_Func.R")
source("~/Project_Master/Test_Rep/Code/Functions/Grapher_Analysis_I.R")


```

### Soil Solution Results
<br>

```{r, message=FALSE, echo=FALSE, results="hide", include=FALSE}
                                              ##Table 1##

SS_Yr_Avg<-Tab_Func_SS_Yr(Cal_Pretable_SS)

SS_Yr_Avg<-mutate(SS_Yr_Avg, group_id=recode(group_id, "'10'='Layer 1' ; '11'='Layer 2' ; '12'='Layer 3' ; '13'='Layer 4'; '14'='Layer 5'; '15'='Layer 6'; '16'='Layer 7'; '17'='Layer 8'"))

SS_Yr_Avg %>% mutate_if(is.numeric, format, digits=2,nsmall = 0) %>%
  kbl(caption = "Table 1: Average Annual Soil Solution Concentration", col.names=c("Soil Layer", "Year", "Ca", "Mg", "K", "Na", "NO3", "NH4", "SO4", "Cl", "PO4", "DOC", "Al", "Si", "H+", "pH", "R", "HR")) %>%t(.)%>%       kable_styling("striped") %>%
    kable_classic(full_width = F, html_font = "Times")
```

<br><br><br>

```{r, message=FALSE, echo=FALSE, results="hide", include=FALSE}

                                               ##Table 2##
SS_Reliable_Avg<-Tab_Func_SS_Reliable(Cal_Pretable_SS)

SS_Reliable_Avg<-mutate(SS_Reliable_Avg, group_id=recode(group_id, "'10'='Layer 1' ; '11'='Layer 2' ; '12'='Layer 3' ; '13'='Layer 4'; '14'='Layer 5'; '15'='Layer 6'; '16'='Layer 7'; '17'='Layer 8'")) %>% select(-X)

SS_Reliable_Avg %>% mutate_if(is.character, format, digits=3,nsmall = 0) %>%
  kbl(caption = "Table 2: Average Monthly Soil Solution Concentration (2005-2006)", col.names=c("Soil Layer","Month", "Ca", "Mg", "K", "Na", "NO3", "NH4", "SO4", "Cl", "PO4", "DOC", "Al", "Si", "H+", "pH", "R", "HR"), "latex") %>%
  t(.)%>% kable_styling(latex_options = c("striped", "scale_down", "hold_position")) %>% 
    kable_classic(full_width = F, html_font = "Times") %>% add_header_above(c(" "=2,  "$\\\\u$mol/L"=16))
```

```{r, echo=FALSE, message=FALSE}
##Average 2005-2006 per layer

Reliable_Table<-SS_Reliable_Avg %>% ungroup(Month) %>% group_by(group_id) %>% summarise(across(Ca:HR, ~ mean(.x, na.rm = TRUE)))

#Change pH average (else it won't make sense!)
Reliable_Table$pH = -log(Reliable_Table$H*10^-6, 10)

Reliable_Table %>% mutate_if(is.numeric, format, digits=3,nsmall = 0) %>%
  kbl(caption = "Average Soil Solution Concentrations of Reliable Months (2005-2006)", col.names=c("Soil Layer", "Ca", "Mg", "K", "Na", "NO3", "NH4", "SO4", "Cl", "PO4", "DOC", "Al", "Si", "H+", "pH", "R", "HR"), align = "l", format="latex", booktabs = TRUE) %>%t(.)%>% kable_styling(latex_options = c("striped", "scale_down", "hold_position")) %>%
    kable_classic(full_width = F, html_font = "Times") %>% add_header_above(c(" "=1,  "$\\\\mu$mol/L"=16))
```


<br><br><br>


```{r, echo=FALSE, fig.cap="Figure 1: Monthly Calcium Concentrations by Soil Layer", figures-side, fig.show="hold", out.width="50%", message=FALSE}

Ca_L1<-Ca_SS_L1(Cal_Pretable_SS_Yr)
Ca_L1

Ca_L2<-Ca_SS_L2(Cal_Pretable_SS_Yr)
Ca_L2


```
```{r, echo=FALSE, fig.cap="Figure 2: Monthly Magnesium Concentrations by Soil Layer", fig.show="hold", out.width="50%"}
Mg_L1<-Mg_SS_L1(Cal_Pretable_SS_Yr)
Mg_L1

Mg_L2<-Mg_SS_L2(Cal_Pretable_SS_Yr)
Mg_L2
```
```{r, echo=FALSE, fig.cap="Figure 3: Monthly Potassium Concentrations by Soil Layer", fig.show="hold", out.width="50%"}


K_L1<-K_SS_L1(Cal_Pretable_SS_Yr)
K_L1

K_L2<-K_SS_L2(Cal_Pretable_SS_Yr)
K_L2

```
```{r, echo=FALSE, fig.cap="Figure 4: Monthly Sodium Concentrations by Soil Layer", fig.show="hold", out.width="50%"}


Na_L1<-Na_SS_L1(Cal_Pretable_SS_Yr)
Na_L1

Na_L2<-Na_SS_L2(Cal_Pretable_SS_Yr)
Na_L2


```

<br><br><br>

```{r, echo=FALSE, fig.cap="Figure 5: Monthly Aluminum Concentrations by Soil Layer", fig.show="hold", out.width="50%"}


Al_L1<-Al_SS_L1(Cal_Pretable_SS_Yr)
Al_L1

Al_L2<-Al_SS_L2(Cal_Pretable_SS_Yr)
Al_L2

```

<br><br><br>

```{r, echo=FALSE, fig.cap="Figure 6: Monthly SiO2 Concentrations by Soil Layer", fig.show="hold", out.width="50%"}

Si_L1<-Si_SS_L1(Cal_Pretable_SS_Yr)
Si_L1

Si_L2<-Si_SS_L2(Cal_Pretable_SS_Yr)
Si_L2

```

<br><br><br>

```{r, echo=FALSE, fig.cap="Figure 7: Monthly Organic Acid Base (R-) Concentrations by Soil Layer", fig.show="hold", out.width="50%"}


R_L1<-R_SS_L1(Cal_Pretable_SS_Yr)
R_L1

R_L2<-R_SS_L2(Cal_Pretable_SS_Yr)
R_L2

```

<br><br><br>

```{r, echo=FALSE, fig.cap="Figure 8: Monthly pH by Soil Layer", fig.show="hold", out.width="50%"}


pH_L1<-pH_SS_L1(Cal_Pretable_SS_Yr)
pH_L1

pH_L2<-pH_SS_L2(Cal_Pretable_SS_Yr)
pH_L2

```
<br><br><br>


### Weathering Results
<br>
```{r, echo=FALSE, message=FALSE, fig.show="Hide", results="Hide", include=FALSE}
                                               ##Table 3##
Year_W_Sum<-Tab_Func_W_Yr(Cal_Pretable_W)


Year_W_Sum %>% mutate_if(is.numeric, format, digits=2,nsmall = 0) %>%
  kbl(caption ="Table 3: Total Annual Weathering", booktabs = TRUE)%>%
    add_header_above(c(" "=1, "(kg/ha)" = 7)) %>%
    t(.)%>% kable_styling("striped") %>%
    kable_classic(full_width = F, html_font = "Times")
```
#### Figures
<br>
```{r, echo=FALSE, message=FALSE, fig.show="hold", out.width="50%", fig.cap="Figure 9: Calcium Weathering by Layer"}
Weathering_Ca1<-Ca_W_L1(Cal_Pretable_W)
Weathering_Ca1

Weathering_Ca2<-Ca_W_L2(Cal_Pretable_W)
Weathering_Ca2



```
<br>
```{r, echo=FALSE, fig.show="hold", out.width="50%", fig.cap="Figure 10: Magnesium Weathering by Layer"}
Weathering_Mg1<-Mg_W_L1(Cal_Pretable_W)
Weathering_Mg1

Weathering_Mg2<-Mg_W_L2(Cal_Pretable_W)
Weathering_Mg2

```
<br>

```{r, echo=FALSE, fig.show="hold", out.width="50%", fig.cap="Figure 11: Potassium Weathering by Layer"}

#K Weathering

```

<br>

```{r, echo=FALSE, fig.show="hold", out.width="50%", fig.cap="Figure 12: Aluminum Weathering by Layer"}
Weathering_Al1<-Al_W_L1(Cal_Pretable_W)
Weathering_Al1

Weathering_Al2<-Al_W_L2(Cal_Pretable_W)
Weathering_Al2

```

<br>

```{r, echo=FALSE, fig.show="hold", out.width="50%", fig.cap="Figure 13: Phosphate Weathering by Layer"}
Weathering_P1<-P_W_L1(Cal_Pretable_W)
Weathering_P1

Weathering_P2<-P_W_L2(Cal_Pretable_W)
Weathering_P2

```

<br>

```{r, echo=FALSE, fig.show="hold", out.width="50%", fig.cap="Figure 14: Silica Weathering by Layer"}
Weathering_Si1<-Si_W_L1(Cal_Pretable_W)
Weathering_Si1

Weathering_Si2<-Si_W_L2(Cal_Pretable_W)
Weathering_Si2

```

<br>

```{r, echo=FALSE, fig.show="hold", out.width="50%", fig.cap="Figure 15: Sodium Weathering by Layer"}
Weathering_Na1<-Na_W_L1(Cal_Pretable_W)
Weathering_Na1

Weathering_Na2<-Na_W_L2(Cal_Pretable_W)
Weathering_Na2

```


<br><br><br>

### Soil Organic Matter (SOM) Results
<br>

```{r, echo=FALSE, fig.cap="Figure 16: SOM Carbon Per Month ", fig.show="hold", out.width="50%"}



```

<br><br><br>

### Litter Pool Results
<br>

```{r, echo=FALSE, fig.show="Hide", results="Hide", include=FALSE}

Litter_Pretable2<-Litter_Pretable %>% select(-Date)

Litter_Pretable2 %>% mutate_if(is.numeric, format, digits=2,nsmall = 0) %>% rename(Year = YEAR)%>%
  kbl(caption ="<b>Table 4: Litter Pool Content<b>", booktabs = TRUE)%>%
    add_header_above(c(" "=2, "(kg/ha)" = 8)) %>%
    t(.)%>% kable_styling("striped") %>%
    kable_classic(full_width = F, html_font = "Times") %>% footnote("These values show the total amount of each species contain in the whole litter (Residue, Coarse Litter, Fine Litter, and Humus")


```

<br><br><br>

```{r, echo=FALSE, fig.cap="Figure 17: Litter Pool Carbon Content Over Simulation Period", fig.show="hold", out.width="50%"}

##Should add specfic fraction over time as well. 

Litter_C<-Litter_Graph(Litter_Pretable$C)
Litter_C+labs(y="C (kg/ha)")

```



```{r, echo=FALSE, fig.cap="Figure 18: Litter Pool Ca Content Over Simulation Period", fig.show="hold", out.width="50%"}

Litter_Ca<-Litter_Graph(Litter_Pretable$Ca)
Litter_Ca+labs(y="Ca (kg/ha)")

```



```{r,echo=FALSE, fig.cap="Figure 19: Litter Pool Mg Content Over Simulation Period", fig.show="hold", out.width="50%"}

Litter_Mg<-Litter_Graph(Litter_Pretable$Mg)
Litter_Mg+labs(y="Mg (kg/ha)")

```


```{r, echo=FALSE, fig.cap="Figure 20: Litter Pool K Content Over Simulation Period", fig.show="hold", out.width="50%"}

Litter_K<-Litter_Graph(Litter_Pretable$K)
Litter_K+labs(y="K (kg/ha)")


```



```{r, echo=FALSE, fig.cap="Figure 21: Litter Pool P Content Over Simulation Period", fig.show="hold", out.width="50%"}

Litter_P<-Litter_Graph(Litter_Pretable$P)
Litter_P+labs(y="P (kg/ha)")


```



```{r, echo=FALSE, fig.cap="Figure 22: Litter Pool S Content Over Simulation Period", fig.show="hold", out.width="50%"}

Litter_S<-Litter_Graph(Litter_Pretable$S)
Litter_S+labs(y="S (kg/ha)")


```
<br><br><br>

### Tree Nutrient Content
<br>

```{r, echo=FALSE, fig.cap="Figure 23: Tree Nutrient Content (kg/ha) in the Foliage", out.width="50%", fig.show="hold", fig.align='center', fig.ncol = 2}
Fol_Nut<-Tree_kg_ha_(Tree_Foliage)
Fol_Nut+labs(fill="Nutrient", y="Total Foliar Nutrient Content (kg/ha)")

Fol_Bi<-Tree_kg_ha_N_Bio(Tree_Foliage)
Fol_Bi+labs(y=expression(Foliar~Biomass~(kg/ha)))

FolN<-Tree_kg_ha_N_(Tree_Foliage)
FolN+labs(y="Foliar N (kg/ha)")


```

<br><br><br>

```{r, echo=FALSE, fig.cap="Figure 24: Tree Nutrient Content (kg/ha) in the Bole. Exlcudes Bark", out.width="50%",fig.align='center', fig.show="hold", fig.ncol = 2}
Bol_Nut<-Tree_kg_ha_(Tree_Wood)
Bol_Nut+labs(fill="Nutrient", y="Total Bole (minus bark) Nutrient Content (kg/ha)")

Bol_Bi<-Tree_kg_ha_N_Bio(Tree_Wood)
Bol_Bi+labs(y=expression(Wood~Bole~Biomass~(kg/ha)))

BolN<-Tree_kg_ha_N_(Tree_Wood)
BolN+labs(y="Wood Bole N (kg/ha)")

```

<br><br><br>

```{r, echo=FALSE, fig.cap="Figure 25: Tree Nutrient Content (kg/ha) in the Bark", out.width="50%", fig.show="hold", fig.align='center', fig.ncol = 2}
Bark_Nut<-Tree_kg_ha_(Tree_Bark)
Bark_Nut+labs(fill="Nutrient", y="Total Bark Nutrient Content (kg/ha)")

Bark_Bi<-Tree_kg_ha_N_Bio(Tree_Wood)
Bark_Bi+labs(y=expression(Bark~Biomass~(ka/ha)))

BarkN<-Tree_kg_ha_N_(Tree_Bark)
BarkN+labs(y="Bark N (kg/ha)")

```

<br><br><br>

```{r, echo=FALSE, fig.cap="Figure 26: Tree Nutrient Content and Biomass (kg/ha) in all Ligneous Material", fig.align='center', out.width="50%", fig.show="hold", fig.ncol = 2}
Lig_Nut<-Tree_kg_ha_(Tree_Ligneous)
Lig_Nut+labs(fill="Nutrient", y="Total Ligneous Nutrient Content (kg/ha)")

Lig_Bi<-Tree_kg_ha_N_Bio(Tree_Ligneous)
Lig_Bi+labs(y=expression(Total~Ligneous~(kg/ha)))

LigN<-Tree_kg_ha_N_(Tree_Ligneous)
LigN+labs(y="Total Ligneous N (kg/ha)")

```

```{r, echo=FALSE, fig.cap="Litterfall quantity", fig.align='center', out.width="50%", fig.show="hold"}

LF_Yr<-Tab_Func_LF_Yr(Litter_Fall)
#Uses same function as tree biomass compartments

LF_Quant<-Tree_LF(LF_Yr)

LF_Quant+labs(x="Year", y=expression(Total~Annual~Litterfall~(g/m^2)))


```


### Cation Exchange Capacity

Not yet complete

### Anion Exchange Capacity 

Not yet complete

### Leaching Losses
```{r, message=FALSE, echo=FALSE}
Leaching_Table_Graphable<-Tab_Func_LL_Yr(Cal_Pretable_LL)
Leaching_Table_1m<-Leaching_Table_Graphable %>% filter(group_id %in% c(8))

```

<br><br><br>

```{r, echo=FALSE, fig.cap="Annual Leaching Losses of Divalent Base Cations", fig.align = "center", out.width = "50%", fig.subcap=c('Ca Leaching Losses', 'Mg Leaching Losses')}
Ca_LL<-LL_1m(Leaching_Table_1m$Ca)
Ca_LL+labs(x="Year", y="Ca (kg/ha)")

Mg_LL<-LL_1m(Leaching_Table_1m$Mg)
Mg_LL+labs(x="Year", y="Mg (kg/ha)")


```
<br>

```{r, echo=FALSE, fig.cap="Annual Leaching Losses of Monovalent Base Cations", fig.align = "center", out.width = "50%", fig.subcap=c('K Leaching Losses', 'Na Leaching Losses')}
K_LL<-LL_1m(Leaching_Table_1m$K)
K_LL+labs(x="Year", y="K (kg/ha)")

Na_LL<-LL_1m(Leaching_Table_1m$Na)
Na_LL+labs(x="Year", y="Na (kg/ha)")
```

<br>

```{r, echo=FALSE, fig.cap="Annual Leaching Losses of N, P, and S", fig.align = "center", out.width = "50%", fig.subcap=c('N Leaching Losses', 'S Leaching Losses', 'P Leaching Losses'), fig.ncol=2, fig.align="center"}

#kg/ha -S/-N or as SO4/No3/Nh4?
Leaching_Table_1m$Ntot<-Leaching_Table_1m$NH4+Leaching_Table_1m$NO3
N_LL<-LL_1m(Leaching_Table_1m$Ntot)
N_LL+labs(x="Year", y="N Losses (kg/ha)")

S_LL<-LL_1m(Leaching_Table_1m$SO4)
S_LL+labs(x="Year", y="S Losses (kg/ha)")

P_LL<-LL_1m(Leaching_Table_1m$P)
P_LL+labs(x="Year", y="P Losses (kg/ha)")

```



Not yet complete

### Analysis 1

```{r, echo=FALSE, message=FALSE}
#Final Mutation for Analysis 1, must be done AFTER leaching_table_1m is assigned. 

Analysis_Bound<- cbind(Leaching_Table_1m, Analysis_1)

Analysis_1_Ready<-Analysis_Bound %>% group_by(V1) %>% 
    mutate(Ca_Net=Ca_Wet+Ca_WTH+Ca_L_Min+Ca_SOM_Min-Ca_TU-Ca) %>%
    mutate(Mg_Net=Mg_Wet+Mg_WTH+Mg_L_Min+Mg_SOM_Min-Mg_TU-Mg) %>% 
    mutate(K_Net=K_Wet+K_WTH+K_L_Min+K_SOM_Min-K_TU-K+K_Folx) %>%
    mutate(SO4_Net=SO4_Wet+ S_L_Min+S_SOM_Min-S_TU-SO4) %>%
    mutate(N_Net=Ntot_Wet+ N_L_Min+N_SOM_Min-N_TU-SO4) %>%
    mutate(P_Net=P_WTH+ P_L_Min+P_SOM_Min-P_TU-P)

```


```{r, echo=FALSE, fig.subcap=c('Net ecosystem calcium retention graphed with bole biomass', 'Net ecosystem calcium retention graphed with foliar biomass index', 'Net ecosystem calcium retention with Bark Biomass index', 'Net ecosystem calcium retention with Branch Biomass index'), fig.cap="Fuck all!", fig.align='center', out.width="50%", fig.ncol=2}

#Must add biomass of compartments to these graphs!
Ca_Net_Gain<-Analysis_I_Grapher(Analysis_1_Ready$Ca_Net)
Ca_Net_Gain+labs(x="Date", y="Net Ca Gain and Bole Biomass Index (kg/ha)")+ geom_line(Tree_Wood, mapping= aes(y=Dry.weight/10000, x=Year, group=1))

Ca_Net_Gain+labs(x="Date", y="Net Ca Gain and Foliar Biomass Index (kg/ha)")+ geom_line(Tree_Foliage, mapping= aes(y=Dry.weight/10000, x=Year, group=1))

Ca_Net_Gain+labs(x="Date", y="Net Ca Gain and Bark Biomass Index (kg/ha)")+ geom_line(Tree_Bark, mapping= aes(y=Dry.weight/10000, x=Year, group=1))

Ca_Net_Gain+labs(x="Date", y="Net Ca Gain and Branch Biomass Index (kg/ha)")+ geom_line(Tree_Branch, mapping= aes(y=Dry.weight/10000, x=Year, group=1))

```
<br>
```{r, echo=FALSE, fig.subcap=c('Net ecosystem magnesium retention graphed with bole biomass', 'Net ecosystem magnesium retention graphed with foliar biomass index', 'Net ecosystem magnesium retention with Bark Biomass index', 'Net ecosystem magnesium retention with Branch Biomass index'), fig.cap="Net ecosystem Magnesium retention plotted against biomass indeces (kg/ha biomass/10,000)", fig.align='center', out.width="50%", fig.ncol=2}

#Must add biomass of compartments to these graphs!
Mg_Net_Gain<-Analysis_I_Grapher(Analysis_1_Ready$Mg_Net)
Mg_Net_Gain+labs(x="Date", y="Net Mg Gain and Bole Biomass Index (kg/ha)")+ geom_line(Tree_Wood, mapping= aes(y=Dry.weight/10000, x=Year, group=1))

Mg_Net_Gain+labs(x="Date", y="Net Mg Gain and Foliar Biomass Index (kg/ha)")+ geom_line(Tree_Foliage, mapping= aes(y=Dry.weight/10000, x=Year, group=1))

Mg_Net_Gain+labs(x="Date", y="Net Mg Gain and Bark Biomass Index (kg/ha)")+ geom_line(Tree_Bark, mapping= aes(y=Dry.weight/10000, x=Year, group=1))

Mg_Net_Gain+labs(x="Date", y="Net Mg Gain and Branch Biomass Index (kg/ha)")+ geom_line(Tree_Branch, mapping= aes(y=Dry.weight/10000, x=Year, group=1))

```
<br>

```{r, echo=FALSE, fig.subcap=c('Net ecosystem potassium retention graphed with bole biomass', 'Net ecosystem potassium retention graphed with foliar biomass index', 'Net ecosystem potassium retention with Bark Biomass index', 'Net ecosystem potassium retention with Branch Biomass index'), fig.cap="Net ecosystem potassium retention plotted against biomass indeces (kg/ha biomass/10,000)", fig.align='center', out.width="50%", fig.ncol=2}

#Must add biomass of compartments to these graphs!
K_Net_Gain<-Analysis_I_Grapher(Analysis_1_Ready$K_Net)
K_Net_Gain+labs(x="Date", y="Net K Gain and Bole Biomass Index (kg/ha)")+ geom_line(Tree_Wood, mapping= aes(y=Dry.weight/10000, x=Year, group=1))

K_Net_Gain+labs(x="Date", y="Net K Gain and Foliar Biomass Index (kg/ha)")+ geom_line(Tree_Foliage, mapping= aes(y=Dry.weight/10000, x=Year, group=1))

K_Net_Gain+labs(x="Date", y="Net K Gain and Bark Biomass Index (kg/ha)")+ geom_line(Tree_Bark, mapping= aes(y=Dry.weight/10000, x=Year, group=1))

K_Net_Gain+labs(x="Date", y="Net K Gain and Branch Biomass Index (kg/ha)")+ geom_line(Tree_Branch, mapping= aes(y=Dry.weight/10000, x=Year, group=1))

```



Nutrient depletion as a condition is being analyzed using the following metric:

(Uptake Rate +(neg SOM Mineralization)+ Leaching Loss Rate + Net Uptake) = Ecosystem Output Rate

Atmospheric Deposition Rate + Mineral Weathering Rate + Foliar Leaching (K only) = Input Rate

Graph rate of 

Input-Output = Net nutrient gain Rate (- is loss, + is gain) vs. Biomass Acquisition of each compartment


### Analysis 2

Percent biomass reduction from 1st harvest (Biomass at Current Harvest/Biomass achieved 1st harvest)*100= % Reduction/month



### Analysis 3

Nutrient buildup in layers over time (Ca should buildup in top layers)


### Analysis 4

Fraction of whole ecosystem nutrients lost with harvest

(Frac Stand Harvest*(Fract. Bole+Fract.Branch+Frac.Foliar+Frac.Bark)/(Soil CEC+Litter+SOM pool+Mineral Pool?+Tree)




