---
title: 'Calibration Report: Low N Sedimentary Site'
author: "Kaveh Gholamhossein Siah"
date: "10/29/2020"
output:
  pdf_document:
    toc: yes
    toc_depth: 3
    
geometry: margin=2 cm
fig_caption: yes
---
<br><br><br>

```{r global_options, include=FALSE, message=FALSE}
#This global option holds figures in the correct place (stops floating in pdf)
knitr::opts_chunk$set(fig.pos = 'H')

```


```{r, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
library(kableExtra)
library(ggplot2)
library(dplyr)
library(captioner)
library(car)
library(janitor)
library(scales)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}

source("~/Project_Master/Test_Rep/Code/LN_SED/Weathering_LN_SED_Mutator.R")

source("~/Project_Master/Test_Rep/Code/LN_SED/Soil_Soln_LN_SED_Mutator.R")

source("~/Project_Master/Test_Rep/Code/LN_SED/Litter_Pool_Mutator.R")

source("~/Project_Master/Test_Rep/Code/LN_SED/TreeNut_LN_SED_Mutator.R")



                                    ##Load Data, edit data as needed##
#umol/L
Cal_Pretable_SS<-read.csv2("~/Project_Master/Test_Rep/Output/Calibration/Output_LN_SED/Edited Data/Soil_Solution_All2.csv", header=TRUE)
Cal_Pretable_SS<-Cal_Pretable_SS %>% filter(group_id %in% c("10", "11", "12", "13", "14", "15", "16", "17"))
Cal_Pretable_SS$group_id<-as.character(Cal_Pretable_SS$group_id)


#Kg/ha
Cal_Pretable_LL<-Cal_Pretable_SS %>% filter(group_id %in% c("1", "2", "3", "4", "5", "6", "7", "8"))


Cal_Pretable_SS_Yr<-Cal_Pretable_SS %>% group_by(group_id, YEAR) %>% summarise(across(Ca:HR, ~mean(.x, na.rm=TRUE)))

Cal_Pretable_W<-read.csv2("~/Project_Master/Test_Rep/Output/Calibration/Output_LN_SED/Edited Data/Weathering_All.csv", header=TRUE)

Litter_Pretable<-read.csv2("~/Project_Master/Test_Rep/Output/Calibration/Output_LN_SED/Edited Data/Litter_Pool.csv", header=TRUE)
Litter_Pretable$Date<-as.Date(as.character(Litter_Pretable$Date))

Tree_Bark<-read.csv2("~/Project_Master/Test_Rep/Output/Calibration/Output_LN_SED/Edited Data/Tree_Bark.csv", header=TRUE)
Tree_Bark$Date<-as.Date(Tree_Bark$Date)

Tree_Wood<-read.csv2("~/Project_Master/Test_Rep/Output/Calibration/Output_LN_SED/Edited Data/Tree_Wood.csv", header=TRUE)
Tree_Wood$Date<-as.Date(Tree_Wood$Date)

Tree_Branch<-read.csv2("~/Project_Master/Test_Rep/Output/Calibration/Output_LN_SED/Edited Data/Tree_Branch.csv")
Tree_Branch$Date<-as.Date(Tree_Branch$Date)

Tree_Foliage<-read.csv2("~/Project_Master/Test_Rep/Output/Calibration/Output_LN_SED/Edited Data/Tree_FOliage.csv")
Tree_Foliage$Date<-as.Date(Tree_Foliage$Date)


                                            ##Load Functions for Analysis##

source("~/Project_Master/Test_Rep/Code/Functions/Tabulator.R")
source("~/Project_Master/Test_Rep/Code/Functions/Grapher_Cal_Soil_R.R")
source("~/Project_Master/Test_Rep/Code/Functions/Grapher_Cal_Weathering.R")
source("~/Project_Master/Test_Rep/Code/Functions/Grapher_Cal_SOM.R")
source("~/Project_Master/Test_Rep/Code/Functions/Grapher_Litter.R")
source("~/Project_Master/Test_Rep/Code/Functions/Grapher_Bio_Compart.R")

```

### Soil Solution Results
<br>

```{r, message=FALSE, echo=FALSE, results="hide", include=FALSE}
                                              ##Table 1##

SS_Yr_Avg<-Tab_Func_SS_Yr(Cal_Pretable_SS)

SS_Yr_Avg<-mutate(SS_Yr_Avg, group_id=recode(group_id, "'10'='Layer 1' ; '11'='Layer 2' ; '12'='Layer 3' ; '13'='Layer 4'; '14'='Layer 5'; '15'='Layer 6'; '16'='Layer 7'; '17'='Layer 8'"))

SS_Yr_Avg %>% mutate_if(is.numeric, format, digits=2,nsmall = 0) %>%
  kbl(caption = "Table 1: Average Annual Soil Solution Concentration", col.names=c("Soil Layer", "Year", "Ca", "Mg", "K", "Na", "NO3", "NH4", "SO4", "Cl", "PO4", "DOC", "Al", "Si", "H+", "pH", "R", "HR")) %>%t(.)%>%       kable_styling("striped") %>%
    kable_classic(full_width = F, html_font = "Times")
```

<br><br><br>

```{r, message=FALSE, echo=FALSE, results="hide", include=FALSE}

                                               ##Table 2##
SS_Reliable_Avg<-Tab_Func_SS_Reliable(Cal_Pretable_SS)

SS_Reliable_Avg<-mutate(SS_Reliable_Avg, group_id=recode(group_id, "'10'='Layer 1' ; '11'='Layer 2' ; '12'='Layer 3' ; '13'='Layer 4'; '14'='Layer 5'; '15'='Layer 6'; '16'='Layer 7'; '17'='Layer 8'")) %>% select(-X)

SS_Reliable_Avg %>% mutate_if(is.character, format, digits=3,nsmall = 0) %>%
  kbl(caption = "Table 2: Average Monthly Soil Solution Concentration (2005-2006)", col.names=c("Soil Layer","Month", "Ca", "Mg", "K", "Na", "NO3", "NH4", "SO4", "Cl", "PO4", "DOC", "Al", "Si", "H+", "pH", "R", "HR"), "latex") %>%
  t(.)%>% kable_styling(latex_options = c("striped", "scale_down", "hold_position")) %>% 
    kable_classic(full_width = F, html_font = "Times") %>% add_header_above(c(" "=2,  "$\\\\u$mol/L"=16))
```

```{r, echo=FALSE, message=FALSE}
##Average 2005-2006 per layer

Reliable_Table<-SS_Reliable_Avg %>% ungroup(Month) %>% group_by(group_id) %>% summarise(across(Ca:HR, ~ mean(.x, na.rm = TRUE)))

#Change pH average (else it won't make sense!)
Reliable_Table$pH = -log(Reliable_Table$H*10^-6, 10)

Reliable_Table %>% mutate_if(is.numeric, format, digits=3,nsmall = 0) %>%
  kbl(caption = "Table 3: Average Soil Solution Concentrations of Reliable Months", col.names=c("Soil Layer", "Ca", "Mg", "K", "Na", "NO3", "NH4", "SO4", "Cl", "PO4", "DOC", "Al", "Si", "H+", "pH", "R", "HR"), align = "l", format="latex", booktabs = TRUE) %>%t(.)%>% kable_styling(latex_options = c("striped", "scale_down", "hold_position")) %>%
    kable_classic(full_width = F, html_font = "Times") %>% add_header_above(c(" "=1,  "$\\\\mu$mol/L"=16))
```


<br><br><br>


```{r, echo=FALSE, fig.cap="Figure 1: Monthly Calcium Concentrations by Soil Layer", figures-side, fig.show="hold", out.width="50%", message=FALSE}

Ca_L1<-Ca_SS_L1(Cal_Pretable_SS_Yr)
Ca_L1

Ca_L2<-Ca_SS_L2(Cal_Pretable_SS_Yr)
Ca_L2


```
```{r, echo=FALSE, fig.cap="Figure 2: Monthly Magnesium Concentrations by Soil Layer", fig.show="hold", out.width="50%"}
Mg_L1<-Mg_SS_L1(Cal_Pretable_SS_Yr)
Mg_L1

Mg_L2<-Mg_SS_L2(Cal_Pretable_SS_Yr)
Mg_L2
```
```{r, echo=FALSE, fig.cap="Figure 3: Monthly Potassium Concentrations by Soil Layer", fig.show="hold", out.width="50%"}


K_L1<-K_SS_L1(Cal_Pretable_SS_Yr)
K_L1

K_L2<-K_SS_L2(Cal_Pretable_SS_Yr)
K_L2

```
```{r, echo=FALSE, fig.cap="Figure 4: Monthly Sodium Concentrations by Soil Layer", fig.show="hold", out.width="50%"}


Na_L1<-Na_SS_L1(Cal_Pretable_SS_Yr)
Na_L1

Na_L2<-Na_SS_L2(Cal_Pretable_SS_Yr)
Na_L2


```

<br><br><br>

```{r, echo=FALSE, fig.cap="Figure 5: Monthly Aluminum Concentrations by Soil Layer", fig.show="hold", out.width="50%"}


Al_L1<-Al_SS_L1(Cal_Pretable_SS_Yr)
Al_L1

Al_L2<-Al_SS_L2(Cal_Pretable_SS_Yr)
Al_L2

```

<br><br><br>

```{r, echo=FALSE, fig.cap="Figure 6: Monthly SiO2 Concentrations by Soil Layer", fig.show="hold", out.width="50%"}

Si_L1<-Si_SS_L1(Cal_Pretable_SS_Yr)
Si_L1

Si_L2<-Si_SS_L2(Cal_Pretable_SS_Yr)
Si_L2

```

<br><br><br>

```{r, echo=FALSE, fig.cap="Figure 7: Monthly Organic Acid Base (R-) Concentrations by Soil Layer", fig.show="hold", out.width="50%"}


R_L1<-R_SS_L1(Cal_Pretable_SS_Yr)
R_L1

R_L2<-R_SS_L2(Cal_Pretable_SS_Yr)
R_L2

```

<br><br><br>

```{r, echo=FALSE, fig.cap="Figure 8: Monthly pH by Soil Layer", fig.show="hold", out.width="50%"}


pH_L1<-pH_SS_L1(Cal_Pretable_SS_Yr)
pH_L1

pH_L2<-pH_SS_L2(Cal_Pretable_SS_Yr)
pH_L2

```
<br><br><br>


### Weathering Results
<br>
```{r, echo=FALSE, message=FALSE, fig.show="Hide", results="Hide", include=FALSE}
                                               ##Table 3##
Year_W_Sum<-Tab_Func_W_Yr(Cal_Pretable_W)


Year_W_Sum %>% mutate_if(is.numeric, format, digits=2,nsmall = 0) %>%
  kbl(caption ="Table 3: Total Annual Weathering", booktabs = TRUE)%>%
    add_header_above(c(" "=1, "(kg/ha)" = 7)) %>%
    t(.)%>% kable_styling("striped") %>%
    kable_classic(full_width = F, html_font = "Times")
```
#### Figures
<br>
```{r, echo=FALSE, message=FALSE, fig.show="hold", out.width="50%", fig.cap="Figure 9: Calcium Weathering by Layer"}
Weathering_Ca1<-Ca_W_L1(Cal_Pretable_W)
Weathering_Ca1

Weathering_Ca2<-Ca_W_L2(Cal_Pretable_W)
Weathering_Ca2



```
<br>
```{r, echo=FALSE, fig.show="hold", out.width="50%", fig.cap="Figure 10: Magnesium Weathering by Layer"}
Weathering_Mg1<-Mg_W_L1(Cal_Pretable_W)
Weathering_Mg1

Weathering_Mg2<-Mg_W_L2(Cal_Pretable_W)
Weathering_Mg2

```
<br>

```{r, echo=FALSE, fig.show="hold", out.width="50%", fig.cap="Figure 11: Potassium Weathering by Layer"}

#K Weathering

```

<br>

```{r, echo=FALSE, fig.show="hold", out.width="50%", fig.cap="Figure 12: Aluminum Weathering by Layer"}
Weathering_Al1<-Al_W_L1(Cal_Pretable_W)
Weathering_Al1

Weathering_Al2<-Al_W_L2(Cal_Pretable_W)
Weathering_Al2

```

<br>

```{r, echo=FALSE, fig.show="hold", out.width="50%", fig.cap="Figure 13: Phosphate Weathering by Layer"}
Weathering_P1<-P_W_L1(Cal_Pretable_W)
Weathering_P1

Weathering_P2<-P_W_L2(Cal_Pretable_W)
Weathering_P2

```

<br>

```{r, echo=FALSE, fig.show="hold", out.width="50%", fig.cap="Figure 14: Silica Weathering by Layer"}
Weathering_Si1<-Si_W_L1(Cal_Pretable_W)
Weathering_Si1

Weathering_Si2<-Si_W_L2(Cal_Pretable_W)
Weathering_Si2

```

<br>

```{r, echo=FALSE, fig.show="hold", out.width="50%", fig.cap="Figure 15: Sodium Weathering by Layer"}
Weathering_Na1<-Na_W_L1(Cal_Pretable_W)
Weathering_Na1

Weathering_Na2<-Na_W_L2(Cal_Pretable_W)
Weathering_Na2

```


<br><br><br>

### Soil Organic Matter (SOM) Results
<br>

```{r, echo=FALSE, fig.cap="Figure 16: SOM Carbon Per Month ", fig.show="hold", out.width="50%"}



```

<br><br><br>

### Litter Pool Results
<br>

```{r, echo=FALSE, fig.show="Hide", results="Hide", include=FALSE}

Litter_Pretable2<-Litter_Pretable %>% select(-Date)

Litter_Pretable2 %>% mutate_if(is.numeric, format, digits=2,nsmall = 0) %>% rename(Year = YEAR)%>%
  kbl(caption ="<b>Table 4: Litter Pool Content<b>", booktabs = TRUE)%>%
    add_header_above(c(" "=2, "(kg/ha)" = 8)) %>%
    t(.)%>% kable_styling("striped") %>%
    kable_classic(full_width = F, html_font = "Times") %>% footnote("These values show the total amount of each species contain in the whole litter (Residue, Coarse Litter, Fine Litter, and Humus")


```

<br><br><br>

```{r, echo=FALSE, fig.cap="Figure 17: Litter Pool Carbon Content Over Simulation Period", fig.show="hold", out.width="50%"}

##Should add specfic fraction over time as well. 

Litter_C<-Litter_Graph(Litter_Pretable$C)
Litter_C+labs(y="C (kg/ha)")

```



```{r, echo=FALSE, fig.cap="Figure 18: Litter Pool Ca Content Over Simulation Period", fig.show="hold", out.width="50%"}

Litter_Ca<-Litter_Graph(Litter_Pretable$Ca)
Litter_Ca+labs(y="Ca (kg/ha)")

```



```{r,echo=FALSE, fig.cap="Figure 19: Litter Pool Mg Content Over Simulation Period", fig.show="hold", out.width="50%"}

Litter_Mg<-Litter_Graph(Litter_Pretable$Mg)
Litter_Mg+labs(y="Mg (kg/ha)")

```


```{r, echo=FALSE, fig.cap="Figure 20: Litter Pool K Content Over Simulation Period", fig.show="hold", out.width="50%"}

Litter_K<-Litter_Graph(Litter_Pretable$K)
Litter_K+labs(y="K (kg/ha)")


```



```{r, echo=FALSE, fig.cap="Figure 21: Litter Pool P Content Over Simulation Period", fig.show="hold", out.width="50%"}

Litter_P<-Litter_Graph(Litter_Pretable$P)
Litter_P+labs(y="P (kg/ha)")


```



```{r, echo=FALSE, fig.cap="Figure 22: Litter Pool S Content Over Simulation Period", fig.show="hold", out.width="50%"}

Litter_S<-Litter_Graph(Litter_Pretable$S)
Litter_S+labs(y="S (kg/ha)")


```
<br><br><br>

## Tree Nutrient Content
<br>

```{r, echo=FALSE, fig.cap="Figure 23: Tree Nutrient Content (kg/ha) in the Foliage", out.width="50%", fig.show="hold"}
Fol_Nut<-Tree_kg_ha_(Tree_Foliage)
Fol_Nut+labs(fill="Nutrient", y="Total Foliar Nutrient Content (kg/ha)")

Fol_Bi<-Tree_kg_ha_N_Bio(Tree_Foliage)
Fol_Bi+labs(y=expression(Foliar~Biomass~(kg/ha)))

FolN<-Tree_kg_ha_N_(Tree_Foliage)
FolN+labs(y="Foliar N (kg/ha)")


```

<br><br><br>

```{r, echo=FALSE, fig.cap="Figure 24: Tree Nutrient Content (kg/ha) in the Bole. Exlcudes Bark", out.width="50%", fig.show="hold"}
Bol_Nut<-Tree_kg_ha_(Tree_Wood)
Bol_Nut+labs(fill="Nutrient", y="Total Bole (minus bark) Nutrient Content (kg/ha)")

Bol_Bi<-Tree_kg_ha_N_Bio(Tree_Wood)
Bol_Bi+labs(y=expression(Wood~Bole~Biomass~(kg/ha)))

BolN<-Tree_kg_ha_N_(Tree_Wood)
BolN+labs(y="Wood Bole N (kg/ha)")

```

<br><br><br>

```{r, echo=FALSE, fig.cap="Figure 25: Tree Nutrient Content (kg/ha) in the Bark", out.width="50%", fig.show="hold"}
Bark_Nut<-Tree_kg_ha_(Tree_Bark)
Bark_Nut+labs(fill="Nutrient", y="Total Bark Nutrient Content (kg/ha)")

Bark_Bi<-Tree_kg_ha_N_Bio(Tree_Wood)
Bark_Bi+labs(y=expression(Bark~Biomass~(ka/ha)))

BarkN<-Tree_kg_ha_N_(Tree_Bark)
BarkN+labs(y="Bark N (kg/ha)")

```

<br><br><br>

```{r, echo=FALSE, fig.cap="Figure 26: Tree Nutrient Content (kg/ha) in all Ligneous Material", out.width="50%", fig.show="hold"}
Tree_Ligneous$Dry.weight<-Tree_Ligneous$`Dry weight`
Lig_Nut<-Tree_kg_ha_(Tree_Ligneous)
Lig_Nut+labs(fill="Nutrient", y="Total Ligneous Nutrient Content (kg/ha)")

Lig_Bi<-Tree_kg_ha_N_Bio(Tree_Ligneous)
Lig_Bi+labs(y=expression(Total~Ligneous~(kg/ha)))

LigN<-Tree_kg_ha_N_(Tree_Ligneous)
LigN+labs(y="Total Ligneous N (kg/ha)")

```

### Cation Exchange Capacity

Not yet complete

### Anion Exchange Capacity 

Not yet complete

### Leaching Losses

Not yet complete

### Analysis 1

Nutrient depletion as a condition is being analyzed using the following metric:

(Uptake Rate (neg SOM Mineralization)+ Leaching Loss Rate + Net Uptake) = Ecosystem Output Rate

Atmospheric Deposition Rate + Mineral Weathering Rate + Foliar Leaching (K only) = Input Rate

Graph rate of 

Input-Output = Net nutrient gain Rate (- is loss, + is gain) vs. Biomass Acquisition of each compartment


### Analysis 2

Percent biomass reduction from 1st harvest (Biomass at Current Harvest/Biomass achieved 1st harvest)*100= % Reduction/month

Biomass of  




